---
title: "DTW distance"
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    highlight: pygments
    toc: true
    toc_float: true
    df_print: paged
    code-tools: true
    code-fold: true
  github_document:
always_allow_html: true
editor_options: 
  markdown: 
    wrap: sentence #Wrap texts in code cells
---

```{r setup, echo=T, results='hide', message=F, warning=F}
pckgs <- c("plotly", "parallelly", "tidyverse", "plotrix", "hypr", 
           "ggthemes", "RColorBrewer", "ggh4x", "dagitty", "DiagrammeR", "patchwork",
           "DiagrammeRsvg", "rsvg", "brms", "bayestestR", "tidybayes",
           "marginaleffects", "emmeans", "doParallel", "ppcor", "svglite")
pacman::p_load(pckgs, character.only = TRUE)


### Set global options
options(digits = 3) # set the default number of digits to 3
cores = as.integer(detectCores(logical = FALSE) * 0.7) # set the number of cores to use
registerDoParallel(cores=cores) # register the number of cores to use for parallel processing
options(mc.cores = cores)
options(brms.backend = "cmdstanr")  #this will speed up the model fitting

### MCMC options
niter = 20000  #number of iterations
nwu = 2000 #number of warmups

### Rmd settings
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, fig.path="figures_md/speakerB/dtw/")
```

```{r functions, echo=T, results='hide', message=F, warning=F}
########### posterior_beta ############
posterior_beta <- function(model, round_int=TRUE){
  ### extract the posterior draws
  posterior_beta <- model %>% 
    spread_draws(`b_.*`, regex = TRUE) %>%
    mutate(ao_sym = b_conditionAO_Asym + b_conditionAsym_Sym,
           `ao_sym:round_c` = `b_conditionAO_Asym:round_c` + `b_conditionAsym_Sym:round_c`) %>%
    pivot_longer(cols = c("b_Intercept",
                          "ao_sym",
                          "b_conditionAsym_Sym",
                          "b_conditionAO_Asym",
                          "b_round_c",
                          "ao_sym:round_c",
                          "b_conditionAsym_Sym:round_c",
                          "b_conditionAO_Asym:round_c"),
                 names_to = ".variable",
                 values_to = ".value") %>%
    mutate(intercept = str_detect(.variable, "Intercept"),
           component = ifelse(str_detect(.variable, ":"), "Round", 
                              ifelse(str_detect(.variable, "round"), "Round", 
                                     ifelse(str_detect(.variable, "Intercept"), "Intercept",
                                            "Visibility"))))
  
  posterior_beta = posterior_beta %>% filter(component != "Intercept")
  
  posterior_beta = posterior_beta %>% 
    mutate(.variable = recode(.variable, 
                              "b_Intercept" = "Intercept",
                              "ao_sym" = "AO--SymAV",
                              "b_conditionAO_Asym" = "AO--AsymAV",
                              "b_conditionAsym_Sym" = "AsymAV--SymAV",
                              "b_round_c" = "Round",
                              "b_conditionAO_Asym:round_c" = "AO--Asym:Round",
                              "b_conditionAsym_Sym:round_c" = "Asym--Sym:Round",
                              "ao_sym:round_c" = "AO--Sym:Round",
                              ),
           .variable = factor(.variable,
                              levels = c("AO--AsymAV", "AsymAV--SymAV", "AO--SymAV",
                                         "Round", "AO--Asym:Round", 
                                         "Asym--Sym:Round", "AO--Sym:Round")),
           component = factor(component, 
                              levels = c("Intercept", "Visibility", "Round")))
  return(posterior_beta)
}


########### plot_posterior ############
plot_posterior <- function(df_post_beta, interaction=FALSE, include_intercept=FALSE,
                           x_lab = "Coefficient", y_lab = "Effect", title_lab = "",
                           xlim_cond=0.3, xlim_round=0.15, ncol_wrap=1){
  
  ### change variables if only main effects are plotted
  if (interaction == F) {
    # df_post_beta = filter(df_post_beta, !str_detect(.variable, ":"))}
    df_post_beta = filter(df_post_beta, component != "Interaction")}
  
  fill_manual_values = c("steelblue", "steelblue", "steelblue", "steelblue")
  space_option = ifelse(ncol_wrap == 1, "free_y", "fixed")
  
  ### plot the posterior distributions
  p_posterior = ggplot(filter(df_post_beta, component != "Intercept"),
                       aes(x = .value, y = fct_rev(.variable),
                           fill = component)) +
    geom_vline(xintercept = 0, size = 1) +
    stat_halfeye(aes(slab_alpha = intercept),
                 normalize = "panels",
                 slab_alpha = 0.5,
                 .width = c(0.89, 0.95),
                 point_interval = "median_hdi") +
    scale_fill_manual(values = fill_manual_values) +
    scale_slab_alpha_discrete(range = c(0.8, 0.4)) +
    guides(fill = "none", slab_alpha = "none") +
    labs(x = x_lab, y = y_lab, title=title_lab) +
    theme_clean(base_size = 15) +
    theme(axis.text.x = element_text(colour = "black", size = 14),
          axis.text.y = element_text(colour = "black", size = 14),
          axis.title = element_text(size = 13, face = 'bold'),
          axis.title.x = element_text(vjust = -2),
          axis.title.y = element_text(vjust = 2),
          legend.position = "none",
          strip.text = element_text(size = 13, face = 'bold'),
          strip.background = element_blank(),
          plot.title.position = "plot",
          panel.grid.major.x = element_line(color = "grey90",
                                            linetype = "solid",
                                            size = 0.5),
          panel.grid.major.y = element_line(color = "grey90",
                                            linetype = "solid",
                                            size = 0.5),
          plot.background = element_blank(),
          plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
    facet_wrap(vars(component), ncol = ncol_wrap,
               scales = "free", space = space_option) +
    facetted_pos_scales(
      x = list(
        scale_x_continuous(limits = c(-xlim_cond, xlim_cond)),
        scale_x_continuous(limits = c(-xlim_round, xlim_round))
      ))
  
  return(p_posterior)
}



########### pp_update_plot ############
pp_update_plot <- function(post_sample, interaction=TRUE){
  sum = ifelse("b_condition_sumAO_Sym" %in% colnames(post_sample), T, F)
  
  intercept = ggplot(post_sample) +
    geom_density(aes(prior_Intercept), fill="steelblue", color="black",alpha=0.6) +
    geom_density(aes(b_Intercept), fill="#FC4E07", color="black",alpha=0.6) + 
    xlab('Intercept') +
    theme_classic()
  
  ### Visibility condition
  cond1 = ggplot(post_sample) +
    geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
    geom_density(aes(b_conditionAsym_Sym), fill="#FC4E07", color="black",alpha=0.6) + 
    xlab('Asym--Sym') +
    theme_classic()
  cond2 = ggplot(post_sample) +
    geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
    geom_density(aes(b_conditionAO_Asym), fill="#FC4E07", color="black",alpha=0.6) + 
    xlab('AO--Asym') +
    theme_classic()
  
  ### Round
  if (interaction) {
    round = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_round_c), fill="#FC4E07", color="black",alpha=0.6) + 
      xlab('Round') +
      theme_classic()
    cond1_round = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(`b_conditionAsym_Sym:round_c`), fill="#FC4E07", color="black",alpha=0.6) + 
      xlab('Centered Round: Asym--Sym') +
      theme_classic()
    cond2_round = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(`b_conditionAO_Asym:round_c`), fill="#FC4E07", color="black",alpha=0.6) + 
      xlab('Centered Round: AO--Asym') +
      theme_classic()
  }
  
  ### display the plots
  if (interaction==F){
    gridExtra::grid.arrange(intercept, cond1, cond2, ncol=2)
  } else {
    gridExtra::grid.arrange(intercept, cond1, cond2, round, 
                            cond1_round, cond2_round, 
                            ncol=2)
  }
}
```

# =====Data preparation=====
## Load data
### df_dtw
Here, we will load the dtw_distance.csv dataframe.

```{r}
### dtw_distance.csv
fct_columns = c("pair", "referent", 
                "speaker_1", "round_1", "trial_1", "target_1", 
                "speaker_2", "round_2", "trial_2", "target_2")

df_dtw = read_csv("data/dtw_distance_mirrored.csv") %>% 
  mutate(pair = as.numeric(pair),
         target = target_2,
         across(fct_columns, as.factor),
         round = round_2,
         speaker = speaker_2) %>% 
  dplyr::select(pair, round, target, comparison_id, 
                average_distance_xyz, speaker, referent:duration_2) %>% 
  filter(!is.na(round))

head(df_dtw)
```


### df_condition_info
```{r}
### condition info
df_condition_info = read.csv("data/condition_info.csv", stringsAsFactors = TRUE) %>% 
  mutate(pair = factor(pair),
         condition = factor(condition,
                            levels = c("Sym", "Asym", "AO"),
                            labels = c("SymAV", "AsymAV", "AO")))
head(df_condition_info)
```

## Merge dataframes
```{r}
### merge dataframes
df = df_dtw %>% 
  left_join(df_condition_info, by="pair") %>%
  dplyr::select(comparison_id, pair, condition, round, 
                speaker, target, referent, average_distance_xyz) %>% 
  mutate(condition_sum = condition,
         round_c = as.integer(round) - mean(as.integer(round))) #centered round

df_all = df

df = df %>% 
  filter(speaker == "B")
```

<br>

# =====Summarize data=====
## Group by pair * speaker
### mean by condition
```{r}
summarize_data <- function(df){
  df %>% 
    summarize(n = n(),
              # dtw distance
              mean_dis = mean(average_distance_xyz, na.rm = FALSE),
              sd_dis = sd(average_distance_xyz, na.rm = FALSE),
              se_dis = std.error(average_distance_xyz, na.rm = FALSE),
              lci_dis = mean_dis - qt(1 - (0.05 / 2), n - 1) * se_dis,
              uci_dis = mean_dis + qt(1 - (0.05 / 2), n - 1) * se_dis) %>%
    ungroup()
}


### create df where each row represents a pair.
df_by_pair = df_all %>% 
  group_by(pair, condition, speaker) %>% 
  summarize_data()


### create df where each row represents a condition.
df_by_cond = df_all %>% 
  group_by(condition, speaker) %>% 
  summarize_data()

df_by_cond
```

### mean by round
```{r}
### create df where each row represents a pair and a round.
df_by_pair_round = df_all %>% 
  group_by(pair, condition, round, speaker) %>% 
  summarize_data()

### create df where each row represents a round.
df_by_round = df_all %>% 
  group_by(round, speaker) %>% 
  summarize_data()

df_by_round
```

### mean by condition x round
```{r}
### create df where each row represents a condition x round.
df_by_cond_round = df_all %>% 
  group_by(condition, round, speaker) %>% 
  summarize_data()

df_by_cond_round
```

<br>


## Speaker B only
```{r}
#=====condition=====
df_by_pair_B = df %>% 
  group_by(pair, condition) %>% 
  summarize_data()

df_by_cond_B = df %>% 
  group_by(condition) %>% 
  summarize_data()


#=====cond*round=====
df_by_pair_round_B = df %>% 
  group_by(pair, condition, round) %>% 
  summarize_data()

df_by_round_B = df %>% 
  group_by(round) %>% 
  summarize_data()

df_by_cond_round_B = df %>% 
  group_by(condition, round) %>% 
  summarize_data()
```


<br>

********************************************************************************************************************

# =====Data visualization=====
## per speaker
### rcp: dtw distance by condition
```{r rcp_distance}
rcp_distance = df_all %>%
  ggplot(aes(x = condition, y = average_distance_xyz,
             fill = condition)) +
  ggdist::stat_halfeye(adjust = 1, width = 0.3, .width = 0,
                       point_color = NA, alpha = 0.6, justification = -0.5) +
  geom_jitter(aes(x = stage(start = condition, after_scale = x - 0.2)),
              size = 0.2, alpha = 0.3, width = 0.07, height = 0) +
  geom_boxplot(width = .2,
               outlier.shape = NA, 
               alpha = 0.7, 
               color = "black") +
  geom_point(data = df_by_cond, 
             aes(y = mean_dis), 
             shape = 21, size = 3, fill = "white") +
  labs(x="Visibility", 
       y="DTW distance") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 15, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 13, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  facet_grid(~speaker)

rcp_distance
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/dtw/rcp_distance.svg", width=4, height=4, dpi=600)
```

<br>

### bp: dtw distance by condition
```{r bp_distance}
bp_distance = df_all %>%
  ggplot(aes(x = condition, y = average_distance_xyz,
             fill = condition)) +
  geom_jitter(aes(x = stage(start = condition)),
              size = 0.15, alpha = 0.15, width = 0.07, height = 0) +
  geom_boxplot(width = .3,
               outlier.shape = NA, 
               alpha = 0.7, 
               color = "black") +
  geom_point(data = df_by_cond, 
             aes(y = mean_dis), 
             shape = 21, size = 3, fill = "white") +
  labs(x="Visibility", 
       y="DTW distance") +
  scale_y_continuous(limits = c(0, 0.9)) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 15, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 13, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  facet_grid(~speaker)

bp_distance
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/dtw/bp_distance.svg", width=4, height=3.5, dpi=600)
```

<br>

### bp: distance by condition x round
```{r bp_distance_by_cond_round}
bp_distance_by_cond_round = 
  ggplot(df_all, 
         aes(x=round, y = average_distance_xyz, fill = condition)) +
  geom_jitter(aes(x = stage(start = round)), 
              size = 0.3, alpha = 0.2, width = 0.07, height = 0.02) +
  geom_boxplot(width = .5,
               outlier.shape = NA, alpha = 0.7) +
  geom_point(data = df_by_cond_round, 
             aes(y = mean_dis, group = round), 
             shape = 21, size = 2, fill = "white") +
  labs(x = "Round",
       y = "DTW distance") +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  scale_y_continuous(limits = c(0, 0.9)) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 15, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 13, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  facet_grid(rows = vars(speaker),
             cols = vars(condition))

ggplotly(bp_distance_by_cond_round)
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/dtw/bp_distance_by_cond_round.svg", width=6.5, height=3.5, dpi=600)
```

<br>


## speaker B only
### rcp: dtw distance by condition
```{r rcp_distance_B}
rcp_distance = df %>%
  ggplot(aes(x = condition, y = average_distance_xyz,
             fill = condition)) +
  ggdist::stat_halfeye(adjust = 1, width = 0.3, .width = 0,
                       point_color = NA, alpha = 0.6, justification = -0.5) +
  geom_jitter(aes(x = stage(start = condition, after_scale = x - 0.2)),
              size = 0.2, alpha = 0.3, width = 0.07, height = 0) +
  geom_boxplot(width = .2,
               outlier.shape = NA, 
               alpha = 0.7, 
               color = "black") +
  geom_point(data = df_by_cond_B, 
             aes(y = mean_dis), 
             shape = 21, size = 3, fill = "white") +
  labs(x="Visibility", 
       y="DTW distance") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 15, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 13, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

rcp_distance
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/dtw/rcp_distance.svg", width=4, height=4, dpi=600)
```

<br>

### bp: dtw distance by condition
```{r bp_distance_B}
bp_distance = df %>%
  ggplot(aes(x = condition, y = average_distance_xyz,
             fill = condition)) +
  geom_jitter(aes(x = stage(start = condition)),
              size = 0.15, alpha = 0.15, width = 0.07, height = 0) +
  geom_boxplot(width = .3,
               outlier.shape = NA, 
               alpha = 0.7, 
               color = "black") +
  geom_point(data = df_by_cond_B, 
             aes(y = mean_dis), 
             shape = 21, size = 3, fill = "white") +
  labs(x="Visibility", 
       y="DTW distance",
       title = "A. DTW distance across visibility") +
  scale_y_continuous(limits = c(0, 0.9)) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 15, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 13, face = 'bold'),
        plot.title = element_text(face = 'bold'),
        plot.title.position = "plot", # left align the title
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

bp_distance
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/dtw/bp_distance.svg", width=4, height=3.5, dpi=600)
```

<br>

### bp: distance by condition x round
```{r bp_distance_by_cond_round_B}
bp_distance_by_cond_round = 
  ggplot(df, 
         aes(x=round, y = average_distance_xyz, fill = condition)) +
  geom_jitter(aes(x = stage(start = round)), 
              size = 0.3, alpha = 0.2, width = 0.07, height = 0.02) +
  geom_boxplot(width = .5,
               outlier.shape = NA, alpha = 0.7) +
  geom_point(data = df_by_cond_round_B, 
             aes(y = mean_dis, group = round), 
             shape = 21, size = 2, fill = "white") +
  labs(x = "Round",
       y = "DTW distance",
       title = "B. DTW distance across visibility x round") +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  scale_y_continuous(limits = c(0, 0.9)) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 15, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 13, face = 'bold'),
        plot.title.position = "plot", # left align the title
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  facet_grid(cols = vars(condition))

ggplotly(bp_distance_by_cond_round)
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/dtw/bp_distance_by_cond_round.svg", width=6.5, height=3.5, dpi=600)
```

<br>

********************************************************************************************************************

# =====DTW distance=====
## ---Causal model---
We assume the following causal model:

```{r dag, fig.width=4, fig.height=4}
### dag
grViz(
  "digraph {
  graph [ranksep = 0.3]
  node [shape = plaintext]
    X [label = Visibility, fontcolor = forestgreen]
    Y [label = DTW_distance, fontcolor = darkorange]
    Z [label = Round]
  edge [minlen = 2.5]
    {X -> Y
    Z -> Y}
  {rank = same; X; Y}
  }"
)
```

Based on the causal inference theory, including the visibility only as fixed effects can estimate its causal effect on DTW distance. As adding rounds should not influence the estiamtes of visibility, we will include rounds as well.

<br>

## ---Contrast coding---
```{r}
### visibility condition: difference coding
h_cond = hypr(AO_Asym = AsymAV ~ AO,
              Asym_Sym = SymAV ~ AsymAV,
              levels = levels(df$condition))
h_cond

contrasts(df$condition) = contr.hypothesis(h_cond)
```

<br>


## Log-normal: [ppB] condition * round_c
### Prior specification
The mediapipe estimates the locations of each keypoint in the video frame with a number between 0 (top, left) and 1 (bottom, right). As we use normalized dtw distance in which the sum of the distance is normalized by the duration of the annotated gestures, we can assume that most of the dtw distances should be between 0 and 1. Therefore, we expect the mean dtw distance to be around 0.5 and the most likely range of the dtw distance to be between 0 and 1.

Given that the dtw distance cannot be negative, it is not optimal to model the dtw distance with a normal distribution (linear regression). Instead, we will use a log-normal distribution to model the dtw distance. The log-normal distribution is a continuous probability distribution of a random variable whose logarithm is normally distributed. The log-normal distribution is a good choice for modeling the dtw distance because it is always positive and has a long tail to the right.

For log-normal regressions, priors need to be specified on the log scale. As such, we will set a prior for the intercept to be Normal(-0.7, 0.5). This means that we expect the most likely distance score is to be 0.5 (exp(-0.7)) and that the 95% of the time the mean to fall between 0.18 (exp(-1.7)) and 2.01 (exp(0.7)). This prior is weakly informative, as it is still informative about the mean while allowing for a wide range of values.

As for the fixed effects, we will set unbiased priors of Normal(0, 0.2). This means that when the mean distance score is 0.5, we expect it to change to 0.33 (exp(-1.1)) or 0.74 (exp(-0.3)) when x increased by 1 (e.g., contrast between AO--AsymAV conditions). This prior is "unbiased" because we are telling the model that most likely values for the slopes are around 0 (i.e., no effect).

As for the random effects, we will set unbiased priors of Normal(0, 0.5).

We will use LKJ(2) prior for the correlation matrix.

```{r}
priors_rint_dtw = c(
  prior(normal(-0.7, 0.5), class = Intercept),
  prior(normal(0, 0.2), class = b),
  prior(normal(0, 0.2), class = sd),
  prior(normal(0, 0.5), class = sigma))

priors_rslope_dtw = c(
  prior(normal(-0.7, 0.5), class = Intercept),
  prior(normal(0, 0.2), class = b),
  prior(normal(0, 0.2), class = sd),
  prior(normal(0, 0.5), class = sigma),
  prior(lkj(2), class = cor))
```

<br>

### Prior predictive check
```{r}
mln_dtw_prior = brm(average_distance_xyz ~ 1 + condition * round_c +
                      (1+round_c|pair) + (1|target),
                    family = lognormal(),
                    prior = priors_rslope_dtw,
                    sample_prior = "only",
                    data = df,
                    file = "models/speakerB/dtw/mln_dtw_prior")

pp_check(mln_dtw_prior, ndraws = 100) +
  coord_cartesian(xlim = c(0, 3),
                  ylim = c(0, 10))
```

The prior predictive check shows that the model is able to generate data that is consistent with the observed data.

<br>

### Fit the model
```{r}
mln_dtw = brm(average_distance_xyz ~ 1 + condition * round_c +
                (1+round_c|pair) + (1|target),
              family = lognormal(),
              prior = priors_rslope_dtw,
              data = df,
              sample_prior = T,
              warmup = nwu, iter = niter,
              control = list(adapt_delta = 0.9,
                             max_treedepth = 15),
              file = "models/speakerB/dtw/mln_dtw")

model = mln_dtw
summary(model)
bayestestR::hdi(model)
# bayestestR::hdi(model, ci = 0.89)
```

The coefficients show that the visibility condition did not have a reliable effect on the dtw distance.

<br>

### Posterior predictive check
```{r ppd_m1}
pp_check(model, ndraws = 100, 
         type = "dens_overlay_grouped", group = "condition") +
  coord_cartesian(xlim = c(0, 3))
```

The posterior predictive check shows that the model is able to generate data that is overall consistent with the observed data.

<br>

### Posterior distributions
```{r pd_m1}
df_post_beta = posterior_beta(model)

# summarize the posterior distribution
post_beta_summary = df_post_beta %>%
  group_by(.variable) %>%
  summarize(mean = mean(.value),
            est_error = sd(.value),
            lci = quantile(.value, 0.025),
            uci = quantile(.value, 0.975))
post_beta_summary

# visualize the posterior distribution
p_pd = plot_posterior(df_post_beta, interaction = F,
                      title = "C. Posterior distributions",
                      ncol_wrap = 1)
p_pd
```


<br>

### Prior-posterior update plot
```{r update_m1}
post_sample = as_draws_df(model)
pp_update_plot(post_sample)
```

<br>

### Hypothesis testing: Bayes factor
```{r}
### varying priors for sensitivity analysis
prior_size = c("xs", "s", "m", "l", "xl")
prior_sd = c(0.05, 0.1, 0.2, 0.3, 0.5)

### list of hypotheses
hps = c("conditionAO_Asym = 0",
        "conditionAsym_Sym = 0",
        "conditionAO_Asym + conditionAsym_Sym = 0",
        "round_c = 0",
        "conditionAO_Asym:round_c = 0",
        "conditionAsym_Sym:round_c = 0",
        "conditionAO_Asym:round_c + conditionAsym_Sym:round_c = 0")
effects = c("AO--AsymAV", "AsymAV--SymAV", "AO--SymAV", "Round", 
            "AO--AsymAV:Round", "AsymAV--SymAV:Round", "AO--SymAV:Round")

for (i in 1:length(prior_sd)){
  priors = c(
    prior(normal(-0.7, 0.5), class = Intercept),
    set_prior(paste0("normal(0,", prior_sd[i], ")"), class = "b"),
    prior(normal(0, 0.2), class = sd),
    prior(normal(0, 0.5), class = sigma),
    prior(lkj(2), class = cor))
  
  fname = paste0("models/speakerB/dtw/mln_dtw_", prior_size[i])
  fname = gsub("_m", "", fname) # remove "_m" for the medium prior
  
  fit = brm(average_distance_xyz ~ 1 + condition * round_c +
              (1+round_c|pair) + (1|target),
            family = lognormal(),
            prior = priors,
            data = df,
            sample_prior = T,
            save_pars = save_pars(all = TRUE),
            warmup = nwu, iter = niter,
            control = list(adapt_delta = 0.9,
                           max_treedepth = 15),
            file = fname)
  
  ### compute BFs for all hypotheses and store them as dataframe
  for (j in 1:length(hps)){
    h = hypothesis(fit, hps[j])
    # transform the result to dataframe
    result = data_frame(h$hypothesis) %>%
      mutate(size = prior_size[i],
             sd = prior_sd[i],
             Effect = effects[j])
    # combine the result
    if (i==1 & j==1){
      df_results = result
    } else {
      df_results = rbind(df_results, result)}
  }
}

df_results = df_results %>%
  mutate(prior = paste0("N(0, ", sd, ")"),
         BF10 = 1 / abs(Evid.Ratio),
         Effect = factor(Effect,
                         levels = c("AO--SymAV", "AO--AsymAV", "AsymAV--SymAV", "Round",
                                    "AO--SymAV:Round", "AO--AsymAV:Round", "AsymAV--SymAV:Round")),
         Predictor = factor(ifelse(grepl("Round", Effect), "Round", "Visibility"),
                            levels = c("Visibility", "Round")),
         across(where(is.numeric), ~ round(., 3))) %>% 
  dplyr::select(size, sd, prior, 
                Effect, Predictor,
                Estimate, Est.Error,
                `CI.Lower`, `CI.Upper`, BF10) %>%
  arrange(Effect, sd)
```

```{r bf_m1}
#### Plot BFs ####
p_bf = ggplot(filter(df_results, Predictor != "Interaction"), 
       aes(x = factor(sd), y = BF10, group = Effect)) +
  geom_hline(yintercept = 1, linetype="dashed") +
  geom_point(aes(color=Effect)) +
  geom_line(aes(color=Effect)) +
  labs(x = "SD for the prior",
       title = "D. Bayes factors for the effects on DTW distance") +
  facet_wrap(vars(Predictor)) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 15, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "right",
        strip.text = element_text(size = 13, face = 'bold'),
        strip.background = element_blank(),
        plot.title.position = "plot", # left align the title
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  scale_y_log10("Bayes factor (BF10)",
                # limits = c(0.1, 3),
                breaks = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100),
                labels = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100)) +
  guides(color = guide_legend(ncol = 1))

p_bf
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/dtw/bayes_factor_dtw.svg", width=7, height=4)
```

<br>

### Back-transformation
```{r back-transformation}
### obtain model predictions
pred_cond = avg_predictions(model, by = "condition",
                            re_formula = NA)

mean_round = mean(as.integer(df$round))
pred_int = avg_predictions(model, by = c("round_c","condition"),
                           re_formula = NA) %>% 
  mutate(round = factor(as.integer(round_c + mean_round)))
```

<br>

### Visualize model predictions together with data
```{r pred_plot}
bp_distance_model = 
  bp_distance +
  geom_ribbon(data = pred_cond,
              aes(x = condition, y = estimate,
                  ymin = conf.low, ymax = conf.high, group = 1),
              fill = "black", alpha = 0.2) +
  geom_line(data = pred_cond,
            aes(x = condition, y = estimate, group = 1),
            color = "black", size = 0.8)

bp_distance_model
ggsave("figures/speakerB/dtw/bp_distance_model.svg", width=4, height=3.5, dpi=600)


bp_distance_by_cond_round_model = 
  bp_distance_by_cond_round +
  geom_ribbon(data = pred_int,
              aes(x = round, y = estimate,
                  ymin = conf.low, ymax = conf.high, group = condition),
              fill = "black", alpha = 0.2) +
  geom_line(data = pred_int,
            aes(x = round, y = estimate, group = condition),
            size = 0.8)

bp_distance_by_cond_round_model
ggsave("figures/speakerB/dtw/bp_distance_by_cond_round_model.svg", width=6.5, height=3.5, dpi=600)
```

<br>

********************************************************************************************************************

# =====Merge plots=====
```{r merge_plots, fig.width=12, fig.height=8}
design = "AAAABBBBBBB
          CCCCDDDDDDD"

free(bp_distance_model) + 
  free(bp_distance_by_cond_round_model) +
  free(p_pd) + 
  free(p_bf) +
  plot_layout(design = design, heights = c(0.7,1))

# save the plot
ggsave("figures/speakerB/dtw/dtw_combined.svg", width=12, height=9)
```


********************************************************************************************************************

# =====Session info=====
```{r}
sessionInfo()
```






