---
title: "gestural_alignment_rate"
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    highlight: pygments
    toc: true
    toc_float: true
    df_print: paged
    code-tools: true
    code-fold: true
  github_document:
    html_preview: false
always_allow_html: true
editor_options: 
  markdown: 
    wrap: sentence #Wrap texts in code cells
---

```{r setup, echo=T, results='hide', message=F, warning=F}
pckgs <- c("plotly", "parallelly", "tidyverse", "plotrix", "hypr", 
           "ggthemes", "RColorBrewer", "ggh4x", "dagitty", "DiagrammeR", "patchwork",
           "DiagrammeRsvg", "rsvg", "brms", "bayestestR", "tidybayes",
           "marginaleffects", "emmeans", "doParallel", "ppcor", "svglite")
pacman::p_load(pckgs, character.only = TRUE)


### Set global options
options(digits = 3) # set the default number of digits to 3
cores = ifelse(availableCores() < 4, 4L, availableCores())
options(mc.cores = cores)
options(brms.backend = "cmdstanr")  #this will speed up the model fitting

### MCMC options
niter = 20000  #number of iterations
nwu = 2000 #number of warmups

### Rmd settings
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, fig.path="figures_md/speakerB/gest_alignment/")
```

```{r functions, echo=T, results='hide', message=F, warning=F}
########### posterior_beta ############
posterior_beta <- function(model, round_int=TRUE, lex_int=FALSE){
  # check if the model uses round_c or round
  round_term = ifelse("round_c" %in% names(model$data), "round_c", 
                      ifelse("round" %in% names(model$data), "round", NA))
  
  # check if the model includes lex_align_c
  lex = ifelse("lex_align_c" %in% names(model$data), T, F)
  
  ### define columns to select based on the model specification
  select_cols = c("b_Intercept", 
                  "b_conditionAO_Asym", "b_conditionAsym_Sym", "ao_sym")
  if (round_term == "round_c") {
    select_cols = c(select_cols, c("b_round_c"))
    if (round_int == TRUE){
      select_cols = c(select_cols, "ao_sym:round_c",
                      "b_conditionAO_Asym:round_c", "b_conditionAsym_Sym:round_c")
    }
  } else if (round_term == "round") {
    select_cols = c(select_cols,
                    c("b_roundR12", "b_roundR23", "b_roundR34", 
                      "b_roundR45", "b_roundR56"))
    if (round_int == TRUE){
      select_cols = c(select_cols,
                      "b_conditionAO_Asym:roundR12", "b_conditionAO_Asym:roundR23",
                      "b_conditionAO_Asym:roundR34", "b_conditionAO_Asym:roundR45",
                      "b_conditionAO_Asym:roundR56",
                      "b_conditionAsym_Sym:roundR12", "b_conditionAsym_Sym:roundR23",
                      "b_conditionAsym_Sym:roundR34", "b_conditionAsym_Sym:roundR45",
                      "b_conditionAsym_Sym:roundR56",
                      "ao_sym:roundR12", "ao_sym:roundR23", "ao_sym:roundR34",
                      "ao_sym:roundR45", "ao_sym:roundR56")
    }
  }
    
  # add b_lex_align_c if lex is True
  select_cols = if (lex) c(select_cols, "b_lex_align_c") else select_cols
  select_cols = if (lex & lex_int) c(select_cols, "b_lex_align_c:conditionAO_Asym", 
                                      "b_lex_align_c:conditionAsym_Sym", 
                                      "lex_align_c:ao_sym") else select_cols
  
  
  ### extract the posterior draws
  posterior_beta = model %>% 
    spread_draws(`b_.*`, regex = TRUE) %>% 
    mutate(ao_sym = b_conditionAO_Asym + b_conditionAsym_Sym)
  
  if (round_term == "round_c" & round_int == TRUE) {
    posterior_beta = posterior_beta %>% 
      mutate(`ao_sym:round_c` = `b_conditionAO_Asym:round_c` + `b_conditionAsym_Sym:round_c`)
    
  } else if (round_term == "round" & round_int == TRUE) {
    posterior_beta = posterior_beta %>% 
      mutate(`ao_sym:roundR12` = `b_conditionAO_Asym:roundR12` + `b_conditionAsym_Sym:roundR12`,
             `ao_sym:roundR23` = `b_conditionAO_Asym:roundR23` + `b_conditionAsym_Sym:roundR23`,
             `ao_sym:roundR34` = `b_conditionAO_Asym:roundR34` + `b_conditionAsym_Sym:roundR34`,
             `ao_sym:roundR45` = `b_conditionAO_Asym:roundR45` + `b_conditionAsym_Sym:roundR45`,
             `ao_sym:roundR56` = `b_conditionAO_Asym:roundR56` + `b_conditionAsym_Sym:roundR56`)
  }
  
  if (lex & lex_int) {
    posterior_beta = posterior_beta %>% 
      mutate(`lex_align_c:ao_sym` = `b_lex_align_c:conditionAO_Asym` + `b_lex_align_c:conditionAsym_Sym`)
  }
  
  posterior_beta = posterior_beta %>%
    pivot_longer(
      cols = select_cols,
      names_to = ".variable",
      values_to = ".value") %>% 
    mutate(component = case_when(str_detect(.variable, ":") ~ "Interaction",
                                 str_detect(.variable, "round") ~ "Round",
                                 str_detect(.variable, "Intercept") ~ "Intercept",
                                 str_detect(.variable, "lex_align") ~ "N. lex align",
                                 .default = "Visibility"))
  
  ### recode variable names and set factor levels
  fct_levels = c("Intercept",
                 "AO--AsymAV", "AsymAV--SymAV", "AO--SymAV",
                 "Round", "Centered log(round)",
                 "R1--R2", "R2--R3", "R3--R4", "R4--R5", "R5--R6",
                 "Round: AO--AsymAV", "Round: AsymAV--SymAV", "Round: AO--SymAV",
                 "AO--AsymAV:R1--R2", "AO--AsymAV:R2--R3", "AO--AsymAV:R3--R4", 
                 "AO--AsymAV:R4--R5", "AO--AsymAV:R5--R6",
                 "AsymAV--SymAV:R1--R2", "AsymAV--SymAV:R2--R3", "AsymAV--SymAV:R3--R4",
                 "AsymAV--SymAV:R4--R5", "AsymAV--SymAV:R5--R6",
                 "AO--SymAV:R1--R2", "AO--SymAV:R2--R3", "AO--SymAV:R3--R4",
                 "AO--SymAV:R4--R5", "AO--SymAV:R5--R6",
                 "N. lex align", "AO--AsymAV:\n N. lex align", 
                 "AsymAV--SymAV:\n N. lex align", "AO--SymAV:\n N. lex align")
  
  posterior_beta = posterior_beta %>% 
    mutate(.variable = recode(.variable, 
                              "b_Intercept" = "Intercept",
                              "b_conditionAO_Asym" = "AO--AsymAV",
                              "b_conditionAsym_Sym" = "AsymAV--SymAV",
                              "ao_sym" = "AO--SymAV",
                              "b_round_c" = "Round",
                              "b_roundR12" = "R1--R2",
                              "b_roundR23" = "R2--R3",
                              "b_roundR34" = "R3--R4",
                              "b_roundR45" = "R4--R5",
                              "b_roundR56" = "R5--R6",
                              "b_lex_align_c" = "N. lex align",
                              "b_conditionAO_Asym:round_c" = "Round: AO--AsymAV",
                              "b_conditionAsym_Sym:round_c" = "Round: AsymAV--SymAV",
                              "ao_sym:round_c" = "Round: AO--SymAV",
                              "b_conditionAO_Asym:roundR12" = "AO--AsymAV:R1--R2",
                              "b_conditionAO_Asym:roundR23" = "AO--AsymAV:R2--R3",
                              "b_conditionAO_Asym:roundR34" = "AO--AsymAV:R3--R4",
                              "b_conditionAO_Asym:roundR45" = "AO--AsymAV:R4--R5",
                              "b_conditionAO_Asym:roundR56" = "AO--AsymAV:R5--R6",
                              "b_conditionAsym_Sym:roundR12" = "AsymAV--SymAV:R1--R2",
                              "b_conditionAsym_Sym:roundR23" = "AsymAV--SymAV:R2--R3",
                              "b_conditionAsym_Sym:roundR34" = "AsymAV--SymAV:R3--R4",
                              "b_conditionAsym_Sym:roundR45" = "AsymAV--SymAV:R4--R5",
                              "b_conditionAsym_Sym:roundR56" = "AsymAV--SymAV:R5--R6",
                              "ao_sym:roundR12" = "AO--SymAV:R1--R2",
                              "ao_sym:roundR23" = "AO--SymAV:R2--R3",
                              "ao_sym:roundR34" = "AO--SymAV:R3--R4",
                              "ao_sym:roundR45" = "AO--SymAV:R4--R5",
                              "ao_sym:roundR56" = "AO--SymAV:R5--R6",
                              "b_lex_align_c:conditionAO_Asym" = "AO--AsymAV:\n N. lex align",
                              "b_lex_align_c:conditionAsym_Sym" = "AsymAV--SymAV:\n N. lex align",
                              "lex_align_c:ao_sym" = "AO--SymAV:\n N. lex align"),
           .variable = factor(.variable,
                              levels = fct_levels),
           component = factor(component, 
                              levels = c("Intercept", "Visibility", "Round", 
                                         "Interaction", "N. lex align")))
  return(posterior_beta)
}



########### plot_posterior ############
plot_posterior <- function(df_post_beta, interaction=FALSE, include_intercept=FALSE,
                           x_lab = "Coefficient", y_lab = "Effect", title_lab = "",
                           xlim_cond=1.5, xlim_round=2, xlim_lex=0.4, ncol_wrap=1){
  ### change variables if only main effects are plotted
  if (interaction == F) {
    # df_post_beta = filter(df_post_beta, !str_detect(.variable, ":"))}
    df_post_beta = filter(df_post_beta, component != "Interaction")}
  
  fill_manual_values = c("steelblue", "steelblue", "steelblue", "steelblue")
  space_option = ifelse(ncol_wrap == 1, "free_y", "fixed")
  
  ### plot the posterior distributions
  p_posterior = ggplot(filter(df_post_beta, component != "Intercept"),
                       aes(x = .value, y = fct_rev(.variable),
                           fill = component)) +
    geom_vline(xintercept = 0, size = 1) +
    stat_halfeye(aes(slab_alpha = intercept),
                 normalize = "panels",
                 slab_alpha = 0.5,
                 .width = c(0.89, 0.95),
                 point_interval = "median_hdi") +
    scale_fill_manual(values = fill_manual_values) +
    scale_slab_alpha_discrete(range = c(0.8, 0.4)) +
    guides(fill = "none", slab_alpha = "none") +
    labs(x = x_lab, y = y_lab, title=title_lab) +
    theme_clean(base_size = 15) +
    theme(axis.text.x = element_text(colour = "black", size = 14),
          axis.text.y = element_text(colour = "black", size = 14),
          axis.title = element_text(size = 13, face = 'bold'),
          axis.title.x = element_text(vjust = -2),
          axis.title.y = element_text(vjust = 2),
          legend.position = "none",
          strip.text = element_text(size = 14, face = 'bold'),
          strip.background = element_blank(),
          plot.title.position = "plot",
          panel.grid.major.x = element_line(color = "grey90",
                                            linetype = "solid",
                                            size = 0.5),
          panel.grid.major.y = element_line(color = "grey90",
                                            linetype = "solid",
                                            size = 0.5),
          plot.background = element_blank(),
          plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
    facet_wrap(vars(component), ncol = ncol_wrap,
               scales = "free", space = space_option) +
    facetted_pos_scales(
      x = list(
        scale_x_continuous(limits = c(-xlim_cond, xlim_cond)),
        scale_x_continuous(limits = c(-xlim_round, xlim_round)),
        scale_x_continuous(limits = c(-xlim_lex, xlim_lex))
      ))
  
  return(p_posterior)
}



########### pp_update_plot ############
pp_update_plot <- function(post_sample, model_type="nb", interaction=TRUE, 
                           fam_par = TRUE, ncol=3, return_grob=FALSE){
  round_bd = ifelse("b_roundR12" %in% colnames(post_sample), T, F)
  lex_align = ifelse("lex_align" %in% colnames(post_sample), T, F)
  
  # define fill colors manually
  post_sample_temp = post_sample %>% 
    pivot_longer(cols = everything(), names_to = "parameter", values_to = "value") %>% 
    filter(parameter %in% c("b_Intercept", "prior_Intercept")) %>%
    mutate(parameter = factor(parameter, 
                              levels = c("prior_Intercept", "b_Intercept"),
                              labels = c("prior", "posterior")))
  
  ### Intercept
  mean_post = mean(post_sample$b_Intercept)
  intercept = ggplot(post_sample_temp) +
    geom_density(aes(value, fill=parameter), color="black",alpha=0.6) +
    # geom_density(aes(b_Intercept, fill="#FC4E07"), color="black",alpha=0.6) + 
    geom_vline(aes(xintercept = mean_post), linetype = "dashed") +
    scale_fill_manual(values = c("steelblue", "#FC4E07")) +
    labs(x = 'Intercept', fill = '') +
    theme_classic()
  
  ### Visibility condition
  cond1 = ggplot(post_sample) +
    geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
    geom_density(aes(b_conditionAO_Asym), fill="#FC4E07", color="black",alpha=0.6) +
    stat_summary(aes(x = b_conditionAO_Asym, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
    labs(x = 'AO--AsymAV', y = "density") +
    theme_classic()
  cond2 = ggplot(post_sample) +
    geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
    geom_density(aes(b_conditionAsym_Sym), fill="#FC4E07", color="black",alpha=0.6) +
    stat_summary(aes(x = b_conditionAsym_Sym, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
    labs(x = 'AsymAV--SymAV', y = "density") +
    theme_classic()
  cond3 = ggplot(post_sample) +
    geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
    geom_density(aes(ao_sym), fill="#FC4E07", color="black",alpha=0.6) + 
    stat_summary(aes(x = ao_sym, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
    labs(x = 'AO--SymAV', y = "density") +
    theme_classic()
  
  ### Lex align
  if (lex_align) {
    lex = ggplot(post_sample) +
      geom_density(aes(prior_lex_align), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(lex_align), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = lex_align, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'N. lex align', y = "density") +
      # scale_x_continuous(limits = c(-1, 1),
      #                    breaks = c(-1, 0, 1)) +
      theme_classic()}
  
  ### Round
  if (round_bd) {
    r1 = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_roundR12), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = b_roundR12, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'R1--R2', y = "density") +
      theme_classic()
    r2 = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_roundR23), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = b_roundR23, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'R2--R3', y = "density") +
      theme_classic()
    r3 = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_roundR34), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = b_roundR34, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'R3--R4', y = "density") +
      theme_classic()
    r4 = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_roundR45), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = b_roundR45, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'R4--R5', y = "density") +
      theme_classic()
    r5 = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_roundR56), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = b_roundR56, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'R5--R6', y = "density") +
      theme_classic()
  } else if ("b_round_c" %in% colnames(post_sample)) {
    round = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_round_c), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = b_round_c, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'Centered round', y = "density") +
      theme_classic()
  } else {
    round = ggplot(post_sample) +
      geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
      geom_density(aes(b_log_round_c), fill="#FC4E07", color="black",alpha=0.6) + 
      stat_summary(aes(x = b_log_round_c, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
      labs(x = 'Centered log(round)', y = "density") +
      theme_classic()
  }
  
  ### Interaction
  if (interaction) {
    if (round_bd){}
    else if ("b_round_c" %in% colnames(post_sample)) {
      cond1_round = ggplot(post_sample) +
        geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(`b_conditionAsym_Sym:round_c`), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = `b_conditionAsym_Sym:round_c`, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Centered Round: Asym--Sym', y = "density") +
        theme_classic()
      cond2_round = ggplot(post_sample) +
        geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(`b_conditionAO_Asym:round_c`), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = `b_conditionAO_Asym:round_c`, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Centered Round: AO--Asym', y = "density") +
        theme_classic()
      cond3_round = ggplot(post_sample) +
        geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(`ao_sym:round_c`), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = `ao_sym:round_c`, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Centered Round: AO--Sym', y = "density") +
        theme_classic()}
    else {
      cond1_round = ggplot(post_sample) +
        geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(`b_conditionAsym_Sym:log_round_c`), fill="#FC4E07", 
                     color="black",alpha=0.6) + 
        stat_summary(aes(x = `b_conditionAsym_Sym:log_round_c`, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Centered log(round): Asym--Sym', y = "density") +
        theme_classic()
      cond2_round = ggplot(post_sample) +
        geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(`b_conditionAO_Asym:log_round_c`), fill="#FC4E07", 
                     color="black",alpha=0.6) + 
        stat_summary(aes(x = `b_conditionAO_Asym:log_round_c`, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Centered log(round): AO--Asym', y = "density") +
        theme_classic()
      cond3_round = ggplot(post_sample) +
        geom_density(aes(prior_b), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(`ao_sym:log_round_c`), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = `ao_sym:log_round_c`, xintercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Centered log(round): AO--Sym', y = "density") +
        theme_classic()}
  }

  ### Family-specific parameters
  if (fam_par == F) {} 
  else {
    if (model_type == "nb"){
      shape = ggplot(post_sample) +
        geom_density(aes(prior_shape), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(shape), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = shape, x_intercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Shape', y = "density") +
        scale_x_continuous(limits = c(0, 10)) +
        theme_classic()} 
    else if (model_type == "zinb") {
      shape = ggplot(post_sample) +
        geom_density(aes(prior_shape), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(shape), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = shape, x_intercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Shape', y = "density") +
        scale_x_continuous(limits = c(0, 10)) +
        theme_classic()
      zi = ggplot(post_sample) +
        geom_density(aes(prior_zi), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(zi), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = zi, x_intercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Zero-inflation', y = "density") +
        theme_classic()} 
    else if (model_type == "zibt"){
      phi = ggplot(post_sample) +
        geom_density(aes(prior_phi), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(phi), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = phi, x_intercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Precision', y = "density") +
        theme_classic()
      zoi = ggplot(post_sample) +
        geom_density(aes(prior_zoi), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(zoi), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = zoi, x_intercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'Zero-inflation', y = "density") +
        theme_classic()
      coi = ggplot(post_sample) +
        geom_density(aes(prior_coi), fill="steelblue", color="black",alpha=0.6) +
        geom_density(aes(coi), fill="#FC4E07", color="black",alpha=0.6) + 
        stat_summary(aes(x = coi, x_intercept = ..x.., y = 0), 
                 fun = mean, geom = "vline", linetype = "dashed", orientation = "y") +
        labs(x = 'One-inflation', y = "density") +
        theme_classic()}
  }
  
  
  ### define the set of plots to display
  p_list = c(intercept, cond1, cond2, cond3)
  
  if (lex_align == T) {p_list = c(p_list, lex)}
  
  if (round_bd == T) {p_list = c(p_list, r1, r2, r3, r4, r5)} 
  else {p_list = c(p_list, round)}
  
  if (interaction == T & round_bd == F) {
    p_list = c(p_list, cond1_round, cond2_round, cond3_round)} 
    
  if (fam_par == T) {
    if (model_type=="nb") {p_list = c(p_list, shape)} 
    else if (model_type=="zinb") {p_list = c(p_list, shape, zi)} 
    else if (model_type=="zibt") {p_list = c(p_list, phi, zoi, coi)}}
  
  ### show the plot
  wrap_plots(p_list) + 
    plot_layout(guides = "collect", ncol = ncol) & theme(legend.position = "bottom")
}


### ggplotly-based function
interactive_plot <- function(p){
  # use ggplotly only if the output format is not GitHub markdown
  if (knitr::pandoc_to("gfm")) p else ggplotly(p)
}
```


# 1. Data preparation
## 1.1 Load data
```{r}
### trial_info_speaker.csv
df_trial_info = read.csv("data/trial_info_speaker.csv", stringsAsFactors = TRUE) %>% 
  filter(num_words != 0) %>%  # remove trials that were accidentally skipped)
  mutate(pair = factor(pair),
         role = factor(ifelse(speaker == director, "director", "matcher")),
         round_c = as.integer(round) - mean(as.integer(round)),
         round_n = factor(round),
         round = factor(paste0("R", round)),
         log_round = log(as.integer(round)),
         log_round_c = log_round - mean(log_round),
         condition = factor(condition,
                            levels = c("Sym", "Asym", "AO"),
                            labels = c("SymAV", "AsymAV", "AO")),
         condition_sum = condition,
         duration_s = duration_ms / 1000,
         n_words_100 = num_words / 100,
         n_iconic_c = num_iconic_gestures - mean(num_iconic_gestures),
         n_iconic_per_100words = num_iconic_gestures / n_words_100,
         n_iconic_100 = num_iconic_gestures / 100,
         lex_align_c = num_lex_align - mean(num_lex_align),
         lex_align_rate = num_lex_align / n_words_100,
         gest_align_rate_100words = num_gestural_align / n_words_100,
         gest_align_rate = num_gestural_align / num_iconic_gestures) %>% 
  rename(trial_duration_s = duration_s, trial_duration_m = duration_m) %>% 
  filter(speaker == "B")

### condition info
df_condition_info = read.csv("data/condition_info.csv", stringsAsFactors = TRUE) %>% 
  mutate(pair = factor(pair),
         condition = factor(condition,
                            levels = c("Sym", "Asym", "AO"),
                            labels = c("SymAV", "AsymAV", "AO")))
```

<br>


## 1.2 Summarize data
```{r}
summarize_demographics <- function(df) {
  df %>%  
    summarize(total_s = sum(trial_duration_s),
              total_m = total_s / 60,
              ### trial duration ###
              mean_trial_dur_s = mean(trial_duration_s),
              mean_trial_dur_m = mean(trial_duration_m),
              sd_trial_dur_m = sd(trial_duration_m),
              lci_trial_dur_m = mean_trial_dur_m - 1.96 * sd_trial_dur_m / sqrt(n()),
              uci_trial_dur_m = mean_trial_dur_m + 1.96 * sd_trial_dur_m / sqrt(n()),
              ### words ###
              # number of words
              num_words_total = sum(num_words),
              mean_num_words = mean(num_words),
              num_words_100 = mean(num_words / 100),
              sd_num_words = sd(num_words),
              lci_num_words = mean_num_words - 1.96 * sd_num_words / sqrt(n()),
              uci_num_words = mean_num_words + 1.96 * sd_num_words / sqrt(n()),
              num_words_per_min = num_words_total / total_m,
              # number of content words
              num_content_total = sum(num_content_words),
              mean_num_content = mean(num_content_words),
              sd_num_content = sd(num_content_words),
              lci_num_content = mean_num_content - 1.96 * sd_num_content / sqrt(n()),
              uci_num_content = mean_num_content + 1.96 * sd_num_content / sqrt(n()),
              num_content_per_min = num_content_total / total_m,
              ### lexical alignment ###
              # raw frequency
              num_lex_align_total = sum(num_lex_align, na.rm = T),
              mean_num_lex_align = mean(num_lex_align, na.rm = T),
              sd_num_lex_align = sd(num_lex_align, na.rm = T),
              lci_num_lex_align = mean_num_lex_align - 1.96 * sd_num_lex_align / sqrt(n()),
              uci_num_lex_align = mean_num_lex_align + 1.96 * sd_num_lex_align / sqrt(n()),
              num_lex_align_per_min = num_lex_align_total / total_m,
              # rate per 100 words
              mean_lex_align_per_100words = mean(lex_align_rate, na.rm=T),
              sd_lex_align_per_100words = sd(lex_align_rate, na.rm=T),
              se_lex_align_per_100words = std.error(lex_align_rate, na.rm=T),
              lci_lex_align_per_100words = mean_lex_align_per_100words - 1.96 * se_lex_align_per_100words,
              uci_lex_align_per_100words = mean_lex_align_per_100words + 1.96 * se_lex_align_per_100words,
              ### iconic gestures ###
              # raw frequency
              num_iconic_total = sum(num_iconic_gestures, na.rm = T),
              mean_num_iconic = mean(num_iconic_gestures, na.rm = T),
              sd_num_iconic = sd(num_iconic_gestures, na.rm = T),
              lci_num_iconic = mean_num_iconic - 1.96 * sd_num_iconic / sqrt(n()),
              uci_num_iconic = mean_num_iconic + 1.96 * sd_num_iconic / sqrt(n()),
              num_iconic_per_min = num_iconic_total / total_m,
              # rate per 100 words
              mean_iconic_per_100words = mean(n_iconic_per_100words, na.rm=T),
              sd_iconic_per_100words = sd(n_iconic_per_100words, na.rm=T),
              se_iconic_per_100words = std.error(n_iconic_per_100words, na.rm=T),
              lci_iconic_per_100words = mean_iconic_per_100words - 1.96 * se_iconic_per_100words,
              uci_iconic_per_100words = mean_iconic_per_100words + 1.96 * se_iconic_per_100words,
              ### gestural alignment ###
              # raw frequency
              num_gest_align_total = sum(num_gestural_align, na.rm = T),
              mean_num_gest_align = mean(num_gestural_align, na.rm = T),
              sd_num_gest_align = sd(num_gestural_align, na.rm = T),
              lci_num_gest_align = mean_num_gest_align - 1.96 * sd_num_gest_align / sqrt(n()),
              uci_num_gest_align = mean_num_gest_align + 1.96 * sd_num_gest_align / sqrt(n()),
              num_gest_align_per_min = num_gest_align_total / total_m,
              # rate per 100 words
              mean_gest_align_per_100words = mean(gest_align_rate_100words, na.rm=T),
              sd_gest_align_per_100words = sd(gest_align_rate_100words, na.rm=T),
              se_gest_align_per_100words = std.error(gest_align_rate_100words, na.rm=T),
              lci_gest_align_per_100words = mean_gest_align_per_100words - 1.96 * se_gest_align_per_100words,
              uci_gest_align_per_100words = mean_gest_align_per_100words + 1.96 * se_gest_align_per_100words,
              # rate per iconic gestures
              mean_gest_align_prop = mean(gest_align_rate, na.rm=T),
              sd_gest_align_prop = sd(gest_align_rate, na.rm=T),
              se_gest_align_prop = std.error(gest_align_rate, na.rm=T),
              lci_gest_align_prop = mean_gest_align_prop - 1.96 * se_gest_align_prop,
              uci_gest_align_prop = mean_gest_align_prop + 1.96 * se_gest_align_prop,
              ### number of trials ###
              trial_n = n()) %>% 
    ungroup()
}

summarize_dur <- function(df){
  df %>% 
    summarize(mean_dur_m = mean(total_m),
              sd_dur_m = sd(total_m),
              se_dur_m = std.error(total_m),
              lci_dur_m = mean_dur_m - 1.96 * se_dur_m,
              uci_dur_m = mean_dur_m + 1.96 * se_dur_m) %>% 
    ungroup()
}
```

<br>

### mean by condition
```{r}
### demographics by pair
trial_info_pair = df_trial_info %>% 
  group_by(pair) %>% 
  summarize_demographics() %>% 
  left_join(., df_condition_info) %>% 
  dplyr::select(pair, condition, total_s:trial_n)

### calculate mean experiment duration
mean_dur_cond = trial_info_pair %>% 
  group_by(condition) %>% 
  summarize_dur()

### summary statistics
trial_info_cond  = df_trial_info %>% 
  group_by(condition) %>% 
  summarize_demographics() %>% 
  left_join(., mean_dur_cond) %>% 
  dplyr::select(condition, total_m, mean_dur_m:uci_dur_m, 
                everything(), 
                -ends_with("_s"))

trial_info_cond


### export it as csv
tbl = trial_info_cond %>% 
  dplyr::select(!starts_with(c("sd_", "se_", "num_", "trial_")) 
                & !contains("total")) %>% 
  pivot_longer(cols = !condition,
               names_to = "name",
               values_to = "value") %>% 
  mutate(stats = sub("_.*", "", name),
         name = sub("[[:alpha:]]+_", "", name),
         across(where(is.numeric), ~ str_squish(format(round(., 2), scientific = FALSE)))) %>% 
  pivot_wider(names_from = c("condition", "stats"),
              values_from = "value") %>% 
  mutate(SymAV_ci = paste0("[", SymAV_lci, ", ", SymAV_uci, "]"),
         AsymAV_ci = paste0("[", AsymAV_lci, ", ", AsymAV_uci, "]"),
         AO_ci = paste0("[", AO_lci, ", ", AO_uci, "]")) %>% 
  dplyr::select(name, SymAV_mean, SymAV_ci, AsymAV_mean, AsymAV_ci, AO_mean, AO_ci)

write_csv(tbl, "tables/descriptive_B.csv")
```

<br>

### mean by round
```{r}
trial_info_pair_round = df_trial_info %>% 
  group_by(pair, round, round_n) %>%
  summarize_demographics() %>% 
  left_join(., df_condition_info)

### calculate mean round duration
mean_dur_round = trial_info_pair_round %>% 
  group_by(round, round_n) %>% 
  summarize_dur()

trial_info_round = df_trial_info %>% 
  group_by(round, round_n) %>% 
  summarize_demographics() %>% 
  left_join(., mean_dur_round) %>%
  dplyr::select(round, round_n, total_m, mean_dur_m:uci_dur_m, 
                everything(), 
                -ends_with("_s"))

trial_info_round
```

<br>

### mean by condition x round
```{r}
### calculate mean duration by condition x round
mean_dur_cond_round = trial_info_pair_round %>% 
  group_by(condition, round, round_n) %>% 
  summarize_dur()

trial_info_cond_round = df_trial_info %>% 
  group_by(condition, round, round_n) %>% 
  summarize_demographics() %>% 
  left_join(., mean_dur_cond_round) %>%
  dplyr::select(condition, round, round_n,
                total_m, mean_dur_m:uci_dur_m, 
                everything(), 
                -ends_with("_s"))

trial_info_cond_round
```


<br>

******************************

# 3. Contrast coding
```{r}
### visibility condition: difference coding
h_cond = hypr(AO_Asym = AsymAV ~ AO,
              Asym_Sym = SymAV ~ AsymAV,
              levels = levels(df_trial_info$condition))
h_cond

contrasts(df_trial_info$condition) = contr.hypothesis(h_cond)

### round
backward_diff = hypr(R12 = R2 ~ R1,
                     R23 = R3 ~ R2,
                     R34 = R4 ~ R3,
                     R45 = R5 ~ R4,
                     R56 = R6 ~ R5,
                     levels = levels(df_trial_info$round))
backward_diff

contrasts(df_trial_info$round) = contr.hypothesis(backward_diff)


### role (director / matcher)
contrasts(df_trial_info$role) = c(-0.5, 0.5)
contrasts(df_trial_info$role)
```

<br>

**************************************************************************************

# ==== Iconic gestures ====

# 4. Number of iconic gestures
## 4.1 DataViz: frequency
### bp: total by condition
```{r bp_iconic_by_cond}
bp_iconic_by_cond = ggplot(data=trial_info_pair, 
                           aes(x=condition, y=num_iconic_total, fill=condition)) +
  geom_jitter(aes(color = pair), 
              size = 1, alpha = 1, 
              width = 0.07, height = 0) +
  geom_boxplot(width = .2,
               outlier.shape = NA, alpha = 0.7) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  labs(x = "Visibility",
       y = "Total N of iconic gestures per pair") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

interactive_plot(bp_iconic_by_cond)
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/iconic/bp_cond.svg", dpi=600, width=6, height=4)
```

<br>


### bp: mean by condition
```{r bp_mean_iconic_by_cond}
bp_mean_iconic_by_cond = ggplot(data=trial_info_pair, 
                                aes(x=condition, y=mean_num_iconic, fill=condition)) +
  geom_jitter(aes(color = pair), 
              size = 1, alpha = 1, 
              width = 0.07, height = 0) +
  geom_boxplot(width = .2,
               outlier.shape = NA, alpha = 0.7) +
  geom_point(data = trial_info_cond, 
             aes(y = mean_num_iconic), 
             shape = 21, size = 3, fill = "white") +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  labs(x = "Visibility",
       y = "Mean N. iconic gest per trial") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

interactive_plot(bp_mean_iconic_by_cond)
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/iconic/bp_mean_cond.svg", dpi=600, width=4, height=3.5)
```

<br>

### bp: mean by condition x round
```{r bp_mean_iconic_by_round_cond}
bp_mean_iconic_by_round_cond = ggplot(data=df_trial_info, 
                                      aes(x=round, y=num_iconic_gestures, fill=condition)) +
  geom_boxplot(outlier.shape = NA,
               alpha = 0.7) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  scale_y_continuous(limits = c(0, 15), breaks = seq(0, 15, 5)) +
  labs(x = "Round",
       y = "Mean N of iconic gestures per trial") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "top",
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

bp_mean_iconic_by_round_cond
```

The figure shows that the decline in iconic gestures across rounds does not follow a linear pattern. This suggests that log-transformed round may improve the model fit.

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/iconic/bp_mean_round_cond.svg", dpi=600, width=6, height=4)
```



<br>

******************************

# 5. Rate of iconic gestures per 100 words
## 5.1 DataViz:Rate per 100 words
### bp: mean by condition
```{r bp_mean_iconic_rate}
bp_mean_iconic_rate = 
  ggplot(data=trial_info_pair, 
         aes(x=condition, y=mean_iconic_per_100words, fill=condition)) +
  geom_jitter(aes(color = pair), 
              size = 1, alpha = 1, 
              width = 0.07, height = 0) +
  geom_boxplot(width = .2,
               outlier.shape = NA, alpha = 0.7) +
  geom_point(data = trial_info_cond, 
             aes(y = mean_iconic_per_100words), 
             shape = 21, size = 3, fill = "white") +
  scale_y_continuous(limits = c(0, 8.1), breaks = seq(0, 8, 2)) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  labs(x = "Visibility",
       y = "Mean rate of iconic gestures") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

interactive_plot(bp_mean_iconic_rate)
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/iconic/bp_mean_iconic_rate.svg", width=6, height=4, dpi=600)
```

<br>

### bp: mean by condition x round
```{r bp_mean_rate_cond_round}
pd = position_dodge(width = .75)

bp_mean_iconic_rate_cond_round = 
  ggplot(data=df_trial_info, 
         aes(x=round_n, y=n_iconic_per_100words, fill=condition)) +
  geom_boxplot(outlier.shape = NA,
               alpha = 0.7) +
  geom_point(data = trial_info_cond_round, 
             aes(y = mean_iconic_per_100words, 
                 group = condition),
             position = pd,
             shape = 21, size = 2, fill = "white") +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  scale_y_continuous(limits = c(0, 22), breaks = seq(0, 20, 5)) +
  labs(x = "Round",
       y = "Mean rate of iconic gestures") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "top",
        strip.background = element_blank(),
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

bp_mean_iconic_rate_cond_round
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/iconic/bp_mean_rate_cond_round.svg", width=6, height=4, dpi=600)
```

<br>


## 5.2 Negative binomial regression models
In the previous section, we analyzed the number of iconic gestures produced per trial. However, it is common to analyze the rate of iconic gestures per 100 words to account for the differences in the length of the trials and speech rate. Here, we will include the log of speech rate (number of words / 100) as an exposure variable and analyze the rate of iconic gestures per 100 words by condition. Note that the syntax for the exposure variable is different from the Poisson regression model; for negative binomial regression, the exposure variable is included with the rate() function.

<br>

### 5.2.1 Prior specification
As the unit of the dependent variable is different from the previous model, we will set different priors for the rate of iconic gestures per 100 words. We will use weakly informative priors for the regression each parameter. To specify priors for the intercept, we will refer to the number of iconic gestures and words reported in Akamine et al. (2024). In the paper, the authors analyzed data from 19 dyads involving in the same task as the current study but in co-present interaction. The total number of iconic gestures reported was 4413, which was collected from 19 dyads, each performing 96 trials. The total number of words produced was 71695 (28152 content) words. Therefore, the expected rate of iconic gestures per 100 words per speaker is $4413 / (71695 / 100) / 2 = 3.08$ (log(3.08) = 1.12).

For the fixed effects, we will set unbiased priors with a mean of 0 and a standard deviation of 0.5.

For the standard deviation of the random effects, we set the prior to be normal with mean 0 and standard deviation 0.5. For the correlation between the random effects, we set the prior to be LKJ(2).

For the models including the round as fixed effects (whether backward-difference coded or centered + log-transformed), the intercept will represent the mean expected number of iconic gestures (ground mean). As the meaning of the intercept doesn't change when adding the round variable, we use the same prior for the intercept. 

Note that we do not expect the rate of iconic gestures to change across rounds (i.e., we expect the number of words and gestures to decrease at an approximately same pace across the rounds). Also, it is common to set the mean of slopes to be 0 to avoid favoring any directions. Therefore we will set the mean of the prior for slope to 0.

```{r}
priors_rslope_rate = c(
  prior(normal(1.12, 0.5), class = Intercept),
  prior(normal(0, 0.5), class = b),
  prior(normal(0, 0.5), class = sd),
  prior(lkj(2), class = cor),
  prior(normal(0, 50), class = shape))

priors_rslope_rate_zinb = c(
  prior(normal(1.12, 0.5), class = Intercept),
  prior(normal(0, 0.5), class = b),
  prior(normal(0, 0.5), class = sd),
  prior(lkj(2), class = cor),
  prior(normal(0, 0.5), class = zi), # on the logit scale
  prior(normal(0, 50), class = shape))
```

<br>


### 5.2.2  Model comparison
#### Round
```{r}
nb_iconic_rate_cond_round = 
  brm(num_iconic_gestures | rate(n_words_100) ~ 
        1 + condition * round + 
        (1+round|pair) + (1|target),
      family = negbinomial(),
      prior = priors_rslope_rate,
      data = df_trial_info,
      sample_prior = T,
      warmup = nwu, iter = niter,
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 15),
      file = "models/speakerB/iconic/nb_iconic_rate_cond_round")

nb_iconic_rate_cond_round_c = 
  brm(num_iconic_gestures | rate(n_words_100) ~ 
        1 + condition * round_c + 
        (1+round_c|pair) + (1|target),
      family = negbinomial(),
      prior = priors_rslope_rate,
      data = df_trial_info,
      sample_prior = T,
      warmup = nwu, iter = niter,
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 15),
      file = "models/speakerB/iconic/nb_iconic_rate_cond_round_c")

nb_iconic_rate_cond_round_log = 
  brm(num_iconic_gestures | rate(n_words_100) ~ 
        1 + condition * log_round_c + 
        (1+log_round_c|pair) + (1|target),
      family = negbinomial(),
      prior = priors_rslope_rate,
      data = df_trial_info,
      sample_prior = T,
      warmup = nwu, iter = niter,
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 15),
      file = "models/speakerB/iconic/nb_iconic_rate_cond_round_log")



### loo compare
if (!file.exists("models/speakerB/iconic/loo_nb_iconic_rate_cond_round.rds")){
  nb_cond_round_loo = loo(nb_iconic_rate_cond_round)
  saveRDS(nb_cond_round_loo, file = "models/speakerB/iconic/loo_nb_iconic_rate_cond_round.rds")
}

if (!file.exists("models/speakerB/iconic/loo_nb_iconic_rate_cond_round_c.rds")){
  nb_cond_round_c_loo = loo(nb_iconic_rate_cond_round_c)
  saveRDS(nb_cond_round_c_loo, file = "models/speakerB/iconic/loo_nb_iconic_rate_cond_round_c.rds")
}

if (!file.exists("models/speakerB/iconic/loo_nb_iconic_rate_cond_round_log.rds")){
  nb_cond_round_log_loo = loo(nb_iconic_rate_cond_round_log)
  saveRDS(nb_cond_round_log_loo, file = "models/speakerB/iconic/loo_nb_iconic_rate_cond_round_log.rds")
}

nb_cond_round_loo = readRDS("models/speakerB/iconic/loo_nb_iconic_rate_cond_round.rds")
nb_cond_round_c_loo = readRDS("models/speakerB/iconic/loo_nb_iconic_rate_cond_round_c.rds")
nb_cond_round_log_loo = readRDS("models/speakerB/iconic/loo_nb_iconic_rate_cond_round_log.rds")

loo_compare(nb_cond_round_loo, nb_cond_round_c_loo, nb_cond_round_log_loo)
```

The leave-one-out (LOO) Effect shows that centered round provides a larger predictive power (elpd_diff) and smaller standard error (se_diff) compared to the backward-difference coded round or centered log-transformed round. Therefore, we will use the centered round.

<br>


#### ZI or not
```{r}
zinb_iconic_rate_cond_round_c = 
  brm(num_iconic_gestures ~ 
        1 + condition * round_c + 
        offset(log(n_words_100)) +
        (1+round_c|pair) + (1|target),
      family = zero_inflated_negbinomial(),
      prior = priors_rslope_rate_zinb,
      data = df_trial_info,
      sample_prior = T,
      warmup = nwu, iter = niter,
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 15),
      file = "models/speakerB/iconic/zinb_iconic_rate_cond_round_c")



### loo compare
if (!file.exists("models/speakerB/iconic/loo_zinb_iconic_rate_cond_round_c.rds")){
  zinb_cond_round_c_loo = loo(zinb_iconic_rate_cond_round_c)
  saveRDS(zinb_cond_round_c_loo, file = "models/speakerB/iconic/loo_zinb_iconic_rate_cond_round_c.rds")
}

nb_cond_round_c_loo = readRDS("models/speakerB/iconic/loo_nb_iconic_rate_cond_round_c.rds")
zinb_cond_round_c_loo = readRDS("models/speakerB/iconic/loo_zinb_iconic_rate_cond_round_c.rds")

loo_compare(nb_cond_round_c_loo, zinb_cond_round_c_loo)
```

The leave-one-out (LOO) Effect shows that non-zero-inflation model has a higher predictive power. As such, we will use a negative binomial regression model.

<br>


### 5.2.3 Prior predictive check
```{r pp_check_iconic}
nb_iconic_rate_cond_round_c_prior = 
  brm(num_iconic_gestures | rate(n_words_100) ~ 
        1 + condition * round_c + 
        (1+round_c|pair) + (1|target),
      family = negbinomial(),
      prior = priors_rslope_rate,
      sample_prior = "only",
      data = df_trial_info,
      file = "models/speakerB/iconic/nb_iconic_rate_cond_round_c_prior")

pp_check(nb_iconic_rate_cond_round_c_prior, ndraws = 100, 
         type = "bars_grouped", group = "condition") +
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 1500))
```

The prior predictive check shows that the model generates data that are somewhat similar to the observed data.

<br>

### 5.2.4 Fit the model
```{r}
nb_iconic_rate_cond_round_c = 
  brm(num_iconic_gestures | rate(n_words_100) ~ 
        1 + condition * round_c + 
        (1+round_c|pair) + (1|target),
      family = negbinomial(),
      prior = priors_rslope_rate_nb,
      data = df_trial_info,
      sample_prior = T,
      save_pars = save_pars(all = TRUE),
      warmup = nwu, iter = niter,
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 15),
      file = "models/speakerB/iconic/nb_iconic_rate_cond_round_c")

model = nb_iconic_rate_cond_round_c
summary(model)
# bayestestR::hdi(model)
# bayestestR::hdi(model, ci = 0.89)
```

The coefficients show that the condition does not have a significant effect on the rate of iconic gestures per 100 words. However, there was a significant decrease in the rate of iconic gestures per 100 words across the rounds. This means that the number of iconic gestures decreased more than the number of words did across the rounds. A formal hypothesis testing will be performed later using Bayes factor.

<br>

### 5.2.5 Posterior predictive check
```{r ppd_iconic}
pp_check(model, ndraws = 100, 
         type = "bars_grouped", group = "condition") +
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 1200))

pp_check(model, ndraws = 100, 
         type = "bars_grouped", group = "round_c") +
  coord_cartesian(xlim = c(0, 5),
                  ylim = c(0, 700))
```

<br>


### 5.2.6 Posterior distributions
```{r pd_iconic, fig.width=8, fig.height=7}
df_post_beta = posterior_beta(model)

# summarize the posterior distribution
post_beta_summary = df_post_beta %>%
  group_by(.variable) %>%
  summarize(mean = mean(.value),
            est_error = sd(.value),
            lci = quantile(.value, 0.025),
            uci = quantile(.value, 0.975))
post_beta_summary

# visualize the posterior distribution
plot_posterior(df_post_beta, interaction = F,
               xlim_cond = 1.2, xlim_round = 0.25, xlim_lex = 0.25)
```

```{r, include=FALSE, echo=FALSE}
ggsave(file="figures/speakerB/iconic/posterior_nb_iconic_rate.svg", width=6, height=5, dpi=600)
```

<br>

### 5.2.7 Hypothesis testing: Bayes factor
```{r}
### varying priors for sensitivity analysis
prior_size = c("xs", "s", "m", "l", "xl")
prior_sd = c(0.1, 0.3, 0.5, 1, 1.5)


### list of hypotheses
hps = c("conditionAO_Asym = 0",
        "conditionAsym_Sym = 0",
        "conditionAO_Asym + conditionAsym_Sym = 0",
        "round_c = 0",
        "conditionAO_Asym:round_c = 0",
        "conditionAsym_Sym:round_c = 0",
        "conditionAO_Asym:round_c + conditionAsym_Sym:round_c = 0")
effects = c("AO--AsymAV", "AsymAV--SymAV", "AO--SymAV", "Round", 
            "AO--AsymAV:Round", "AsymAV--SymAV:Round", "AO--SymAV:Round")

for (i in 1:length(prior_sd)){
  priors = c(
    prior(normal(1.12, 0.5), class = Intercept),
    set_prior(paste0("normal(0,", prior_sd[i], ")"), class = "b"),
    prior(normal(0, 0.5), class = sd),
    prior(lkj(2), class = cor),
    prior(normal(0, 50), class = shape))
  
  fname = paste0("models/speakerB/iconic/nb_iconic_rate_cond_round_c_", prior_size[i])
  fname = gsub("_m", "", fname) # remove "_m" for the medium prior
  
  fit = brm(num_iconic_gestures | rate(n_words_100) ~ 
              1 + condition * round_c +
              (1+round_c|pair) + (1|target),
            family = negbinomial(),
            prior = priors,
            data = df_trial_info,
            sample_prior = T,
            save_pars = save_pars(all = TRUE),
            warmup = nwu, iter = niter,
            control = list(adapt_delta = 0.9, 
                           max_treedepth = 15),
            file = fname)
  
  ### compute BFs for all hypotheses and store them as dataframe
  for (j in 1:length(hps)){
    h = hypothesis(fit, hps[j])
    # transform the result to dataframe
    result = data_frame(h$hypothesis) %>%
      mutate(size = prior_size[i],
             sd = prior_sd[i],
             Effect = effects[j])
    # combine the result
    if (i==1 & j==1){
      df_results = result
    } else {
      df_results = rbind(df_results, result)}
  }
}

df_results = df_results %>%
  mutate(prior = paste0("N(0, ", sd, ")"),
         BF10 = 1 / abs(Evid.Ratio),
         Effect = factor(Effect,
                         levels = c("AO--SymAV", "AO--AsymAV", "AsymAV--SymAV", "Round",
                                    "AO--SymAV:Round", "AO--AsymAV:Round", "AsymAV--SymAV:Round")),
         Predictor = factor(ifelse(grepl(":Round", Effect), "Interaction",
                                   ifelse(grepl("Round", Effect), "Round", "Visibility")),
                            levels = c("Visibility", "Round", "Interaction")),
         across(where(is.numeric), ~ round(., 3)),
         Star = ifelse(BF10 >= 30 | BF10 <= 1/30, "***",
                       ifelse(BF10 >= 10 | BF10 <= 1/10, "**",
                              ifelse(BF10 >= 3 | BF10 <= 1/3, "*", ""))),
         Star = ifelse(BF10 < 1, str_replace_all(Star, "[*]", "="), Star)) %>% 
  dplyr::select(size, sd, prior, Effect, Predictor,
                Estimate, Est.Error, `CI.Lower`, `CI.Upper`, BF10, Star) %>% 
  arrange(Effect, sd)
```

```{r bf_iconic_rate}
#### Plot BFs ####
p_bf = ggplot(filter(df_results, Predictor != "Round"), 
              aes(x = factor(sd), y = BF10, group = Effect)) +
  geom_hline(yintercept = 1, linetype="dashed") +
  geom_point(aes(color=Effect)) +
  geom_line(aes(color=Effect)) +
  labs(x = "SD for the prior",
       title = "D. Bayes factors for main effects") +
  facet_wrap(vars(Predictor)) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "right",
        legend.text = element_text(size = 12),
        strip.text = element_text(size = 14, face = 'bold'),
        strip.background = element_blank(),
        plot.title.position = "plot", # left align the title
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  scale_y_log10("Bayes factor (BF10)",
                # limits = c(0.03, 30000),
                breaks = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100, 1e3, 1e4),
                labels = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100, 1e3, 1e4)) +
  guides(color = guide_legend(ncol = 1))

p_bf
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/iconic/bf_iconic_rate.svg", width=8, height=4, dpi=600)
```

<br>

### 5.2.8 Back-transformation
```{r back-transformation}
### obtain model predictions
pred_cond = 
  avg_predictions(model, by = "condition",
                  type = "link", transform = exp,
                  re_formula = NA) %>% 
  as_tibble()
pred_cond

mean_round = mean(as.integer(df_trial_info$round))
pred_int = 
  avg_predictions(model, by = c("round_c","condition"),
                  type = "link", transform = exp,
                  re_formula = NA) %>%
  as_tibble() %>% 
  mutate(round = factor(as.integer(round_c + mean_round)))
pred_int
```


<br>


### 5.2.9 Visualize model predictions together with data
```{r pred_plot}
bp_mean_iconic_rate_model = 
  bp_mean_iconic_rate +
  geom_ribbon(data = pred_cond,
              aes(x = condition, y = estimate,
                  ymin = conf.low, ymax = conf.high, group = 1),
              fill = "black", alpha = 0.2) +
  geom_line(data = pred_cond,
            aes(x = condition, y = estimate, group = 1),
            color = "black", size = 0.8)

bp_mean_iconic_rate_model
ggsave("figures/speakerB/iconic/bp_mean_iconic_rate_model.svg", width=4, height=3.5)


bp_mean_iconic_rate_cond_round_model = 
  bp_mean_iconic_rate_cond_round +
  geom_ribbon(data = pred_int,
              aes(x = round, y = estimate,
                  ymin = conf.low, ymax = conf.high, 
                  group = condition, fill = condition),
              alpha = 0.2) +
  geom_line(data = pred_int,
            aes(x = round, y = estimate, 
                group = condition, color = condition),
            size = 0.8) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  scale_color_manual(values = c("#ED6B06", "#00786A", "darkgrey"))

bp_mean_iconic_rate_cond_round_model
ggsave("figures/speakerB/iconic/bp_mean_iconic_rate_cond_round_model.svg", width=6, height=4)
```

<br>

******************************

# ==== Gestural alignment ====

# 6. Causal model of gestural alignment

Experts in the field of statistics and causal inference have advised that researchers should build a causal model and examine which factors should be included and excluded from regression models if their aim is to infer the causal effects (e.g., [McElreath, 2020](https://www.taylorfrancis.com/books/mono/10.1201/9780429029608/statistical-rethinking-richard-mcelreath), [Pearl, 2010](https://pmc.ncbi.nlm.nih.gov/articles/PMC2836213/), [Cinelli, Forney, & Pearl, 2020](https://journals.sagepub.com/doi/full/10.1177/00491241221099552)). Following this advice, we will build a causal model to infer the direct effect of speaker visibility on gestural alignment.

We assume the following causal model:
```{r dag}
### causal model for gestural alignment rate
dag_gest <- dagitty('dag {
  visibility -> gest_align
  visibility -> n_words
  visibility -> n_gestures
  n_words -> lex_align
  n_words -> n_gestures
  round -> n_words
  round -> lex_align
  round -> gest_align
  round -> n_gestures
  role -> n_words
  role -> lex_align
  role -> gest_align
  role -> n_gestures
  n_gestures -> gest_align
  lex_align -> gest_align
}')

plot(dag_gest)

### check the minimam adjustment set
print("Direct effect of visibility on gestural alignment frequency")
adjustmentSets(dag_gest, exposure = "visibility", outcome = "gest_align", effect = "direct")

print("Direct effect of lexical alignment frequency on gestural alignment frequency")
adjustmentSets(dag_gest, exposure = "lex_align", outcome = "gest_align", effect = "direct")

print("Direct effect of round on gestural alignment frequency")
adjustmentSets(dag_gest, exposure = "round", outcome = "gest_align", effect = "direct")
```

The minimum adjustment set for estimating the direct causal effect of speaker visibility on gestural alignment frequency is {lex_align, n_words, round}. Note that because dagitty didn't find any adjustment set for the direct effect of visibility on lexical alignment frequency *when we expected bidirectional causation between lexical and gestural alignment*, we assumed a unidirectional causation from lexical alignment to gestural alignment only in this model. This will be reversed in the causal model for lexical alignment frequency, such that we assume a unidirectional causation from gestural alignment to lexical alignment. 

In addition, we are also interested in the direct effect of lexical alignment frequency on gestural alignment frequency. The minimum adjustment set for is {visibility, n_gestures, round}.

As the minimum adjustment sets for the direct effects of visibility, lexical alignment frequency, and round on gestural alignment frequency are identical (i.e., {visibility, lex_align, n_gestures, round}), we can estimate the direct effect of these variables on gestural alignment frequency with the following model:

$$
gest\_align \: | \: \text{rate}(n\_iconic\_gesture) \sim \\
\text{visibility} * \text{round} + \text{n_lexical_alignment} + \\
(1+\text{round} | \text{participant}) + (1 | \text{item})
$$

<br>

******************************

# 7. Number of gestural alignment
## 7.1 DataViz: number of gestural alignment
### bp: mean by condition
```{r bp_mean_cpt_cond}
bp_mean_gest_alignment = 
  ggplot(data=trial_info_pair, 
         aes(x=condition, y=mean_num_gest_align, fill=condition)) +
  geom_jitter(aes(color = pair), 
              size = 1, alpha = 1, 
              width = 0.07, height = 0) +
  geom_boxplot(width = .4,
               outlier.shape = NA, alpha = 0.7) +
  geom_point(data = trial_info_cond, 
             aes(y = mean_num_gest_align), 
             size = 2, shape = 4) +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  labs(x = "Visibility",
       y = "Mean gestural alignment count") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

interactive_plot(bp_mean_gest_alignment)
```


```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/gest_alignment/bp_mean_cpt_cond.svg", width=6, height=4, dpi=600)
```

<br>

## 7.2 ZI Negative binomial regression
### 7.2.1 Prior specification
We will set priors for the intercept based on the expected number of gestural alignment reported in Akamine et al. (2024). In the paper, the authors analyzed data from 19 dyads involving in the same task as the current study but in co-present interaction. The total number of gestural alignment reported was 1086, which was collected from 19 dyads, each performing 96 trials. This leads to the expected number of gestural alignment per speaker to be 1086 / (19 * 96) / 2 = 0.3 (log(0.3) = -1.2). As such, we will set the prior for the intercept to be normal with a mean of -1.2 and a standard deviation of 0.5.

For the fixed effects, we will set unbiased priors with a mean of 0. We set different SDs for each effect because the scale of each predictor is different. For N. lexical alignment and N. iconic gestures, we set a prior of Normal(0, 0.2). This means that if the mean N. lex align increases by 1, we expect the mean N. gestural alignment to change by -0.2 to 0.5, with the most likely size of change to be 0. As for the other predictors, we set a prior of Normal(0. 0.5).


We will also specify a prior for the shape parameter to prevent the model from returning divergent transitions. We will set the prior to be normal with a mean of 0 and a wide standard deviation of 50.

For the standard deviation of the random effects, we set the prior to be normal with mean 0 and standard deviation 0.5. For the correlation between the random effects, we set the prior to be LKJ(2).

```{r}
### pair
priors_rslope_gest_align_zinb = c(
  prior(normal(-1.2, 0.5), class = Intercept),
  prior(normal(0, 0.5), class = b),
  prior(normal(0, 0.2), class = b, coef = "n_iconic_c"),
  prior(normal(0, 0.2), class = b, coef = "lex_align_c"),
  prior(normal(0, 0.2), class = b, coef = "lex_align_c:conditionAO_Asym"),
  prior(normal(0, 0.2), class = b, coef = "lex_align_c:conditionAsym_Sym"),
  prior(normal(0, 0.5), class = sd),
  prior(lkj(2), class = cor),
  prior(normal(0, 0.5), class = zi), # on the logit scale
  prior(normal(0, 50), class = shape))
```


<br>

### 7.2.2 Prior predictive check
```{r pp_check_count}
zinb_gest_align_prior = 
  brm(num_gestural_align ~
        1 + lex_align_c * condition + round + n_iconic_c + role +
        (1+round|pair) + (1|target),
      family = zero_inflated_negbinomial(),
      prior = priors_rslope_gest_align_zinb,
      data = df_trial_info,
      sample_prior = "only",
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 20),
      file = "models/speakerB/gest_alignment/zinb_gest_align_prior")

pp_check(zinb_gest_align_prior, ndraws = 100, type = "bars") +
  coord_cartesian(xlim = c(0, 20),
                  ylim = c(0, 4000))
```

The prior predictive check shows that the prior distributions predict data that are similar to the observed data.

<br>

### 7.2.3 Fit the model
```{r}
zinb_align_cond_round = 
  brm(num_gestural_align ~ 
        1 + lex_align_c * condition + round + n_iconic_c + role +
        (1+round|pair) + (1|target),
      family = zero_inflated_negbinomial(),
      prior = priors_rslope_gest_align_zinb,
      data = df_trial_info,
      sample_prior = T,
      save_pars = save_pars(all = TRUE),
      warmup = nwu, iter = niter,
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 15),
      file = "models/speakerB/gest_alignment/zinb_align_cond_round")

model = zinb_align_cond_round
summary(model)
# bayestestR::hdi(model)
```

The coefficients show that the number of lexical alignment is a reliable predictor of the number of gestural alignment.

<br>

### 7.2.4 Posterior predictive check
```{r}
pp_check(zinb_align_cond_round, ndraws = 100, 
         type = "bars_grouped", group = "condition") +
  coord_cartesian(xlim = c(0, 5))

pp_check(zinb_align_cond_round, ndraws = 100,
         type = "bars_grouped", group = "round") +
  coord_cartesian(xlim = c(0, 5))
```

The posterior predictive check shows that the model generates data that are similar to the observed data, demonstrating good model fit.

<br>

### 7.2.5 Hypothesis testing: Bayes factor
```{r}
### varying priors for sensitivity analysis
prior_size = c("xs", "s", "m", "l", "xl")
prior_sd = c(0.05, 0.1, 0.2, 0.3, 0.5)


### list of hypotheses
hps = c("lex_align_c = 0",
        "lex_align_c:conditionAO_Asym = 0",
        "lex_align_c:conditionAsym_Sym = 0",
        "lex_align_c:conditionAO_Asym + lex_align_c:conditionAsym_Sym = 0")
effects = c("N. lex align", "AO--AsymAV:N. lex align", 
            "AsymAV--SymAV:N. lex align", "AO--SymAV:N. lex align")

for (i in 1:length(prior_sd)){
  priors = c(
    prior(normal(-1.2, 0.5), class = Intercept),
    prior(normal(0, 0.5), class = b),
    prior(normal(0, 0.2), class = b, coef = "n_iconic_c"),
    set_prior(paste0("normal(0,", prior_sd[i], ")"), 
              class = "b", coef = "lex_align_c"),
    set_prior(paste0("normal(0,", prior_sd[i], ")"), 
              class = "b", coef = "lex_align_c:conditionAO_Asym"),
    set_prior(paste0("normal(0,", prior_sd[i], ")"), 
              class = "b", coef = "lex_align_c:conditionAsym_Sym"),
    prior(normal(0, 0.5), class = sd),
    prior(lkj(2), class = cor),
    prior(normal(0, 0.5), class = zi),
    prior(normal(0, 50), class = shape))
  
  fname = paste0("models/speakerB/gest_alignment/zinb_align_cond_round_", prior_size[i])
  fname = gsub("_m", "", fname) # remove "_m" for the medium prior
  
  fit = brm(num_gestural_align ~ 
              1 + lex_align_c * condition + round + n_iconic_c + role +
              (1+round|pair) + (1|target),
            family = zero_inflated_negbinomial(),
            prior = priors,
            data = df_trial_info,
            sample_prior = T,
            save_pars = save_pars(all = TRUE),
            warmup = nwu, iter = niter,
            control = list(adapt_delta = 0.9, 
                           max_treedepth = 15),
            file = fname)
  
  ### compute BFs for all hypotheses and store them as dataframe
  for (j in 1:length(hps)){
    h = hypothesis(fit, hps[j])
    # transform the result to dataframe
    result = data_frame(h$hypothesis) %>%
      mutate(size = prior_size[i],
             sd = prior_sd[i],
             Effect = effects[j])
    # combine the result
    if (i==1 & j==1){
      df_results = result
    } else {
      df_results = rbind(df_results, result)}
  }
}

df_bf_lex = df_results %>%
  mutate(prior = paste0("N(0, ", sd, ")"),
         BF10 = 1 / abs(Evid.Ratio),
         Effect = factor(Effect,
                         levels = effects),
         Predictor = factor(ifelse(grepl(":N. lex align", Effect), "Interaction", "N. lex align"),
                            levels = c("N. lex align", "Interaction")),
         across(where(is.numeric), ~ round(., 3)),
         Star = ifelse(BF10 >= 30 | BF10 <= 1/30, "***",
                       ifelse(BF10 >= 10 | BF10 <= 1/10, "**",
                              ifelse(BF10 >= 3 | BF10 <= 1/3, "*", ""))),
         Star = ifelse(BF10 < 1, str_replace_all(Star, "[*]", "="), Star)) %>% 
  dplyr::select(size, sd, prior, Effect, Predictor,
                Estimate, Est.Error, `CI.Lower`, `CI.Upper`, BF10, Star) %>% 
  arrange(Effect, sd)

df_bf_lex
```

```{r bf_freq}
#### Plot BFs ####
ggplot(filter(df_bf_lex, Effect != "N. lex align"),
       aes(x = factor(sd), y = BF10, group = Effect)) +
  geom_hline(yintercept = 1, linetype="dashed") +
  geom_point(aes(color=Effect)) +
  geom_line(aes(color=Effect)) +
  facet_wrap(vars(Predictor)) +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "right",
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  scale_y_log10("Bayes factor (BF10)",
                breaks = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100),
                labels = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100)) +
  xlab("SD for the prior")
```

### 7.2.6 Plot effects of lex alignment on gestural alignment
```{r corr_lex_gest_align, fig.width=5, fig.height=6}
plot_predictions(model,
                 type = "response",
                 condition = c("lex_align_c", "condition"))


### generate model predictions
df_pred = 
  predictions(model,
              by = c("lex_align_c", "condition"),
              newdata = datagrid(condition = unique,
                                 lex_align_c = seq(from = min(df_trial_info$lex_align_c),
                                                   to = max(df_trial_info$lex_align_c)))) %>% 
  mutate(num_lex_align = round(lex_align_c + mean(df_trial_info$num_lex_align), 0))

### aggregate data for plotting
mean_lex_gest_by_cond = df_trial_info %>% 
  group_by(pair, condition, num_lex_align) %>% 
  summarize(num_gestural_align = mean(num_gestural_align)) %>% 
  ungroup()

### plot data with model predictions
lex_gest_cor = 
  ggplot(data = mean_lex_gest_by_cond,
         aes(x = num_lex_align, y = num_gestural_align, 
             color = condition, fill = condition)) +
  geom_jitter(size = 1, alpha = 0.7,
              width = 0.1, height = 0.1) +
  geom_ribbon(data = df_pred,
              aes(y = estimate, 
                  ymin = conf.low, ymax = conf.high),
              alpha = 0.2, color = NA) +
  geom_line(data = df_pred,
            aes(y = estimate),
            linewidth = 1) +
  # scale_x_continuous(limits = c(0, 8)) +
  # scale_y_continuous(limits = c(0, 5)) +
  labs(x = "Mean N. lexical alignment per trial",
       y = "Mean N. gestural alignment per trial") +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  scale_color_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  theme_clean(base_size = 14) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        strip.text = element_text(size = 14, face = 'bold'),
        legend.position = "top",
        legend.title = element_text(size = 13),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1, 1.1), "lines"))

lex_gest_cor
```

Although the data shows a clear positive correlation between lexical alignment and gestural alignment, the model predictions show that the effect is relatively small. This is likely due to the inclusion of other predictors in the model (e.g., n_iconic_gestures, role), which account for some of the variance in gestural alignment.

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/gest_alignment/corr_lex_gest_align.svg", width=5, height=4, dpi=600)
```

<br>

### 7.2.7 Calculate effect size of lexical alignment on gestural alignment
To avoid confounding, we modeled the effect of lexical alignment on the **number** of gestural alignment. However, we will model the others effects on the **rate** of gestural alignment (i.e., number of gestural alignment per iconic gesture). To understand the effect size of lexical alignment on the rate scale so that we can compare it with the effects of other predictors, we will (1) calculate the effect size on the count scale (i.e., response scale), and (2) calculate the proportion of gestural alignment explained by lexical alignment.

The effect size on count scale can be calculated by counterfactual comparisons: we first calculate the predicted number of gestural alignment when the number of lexical alignment is 0 (i.e., lex_0) and when the number of lexical alignment is at the mean (i.e., intercept), and then we calculate the effect size as the difference between intercept and lex_0. This is equivalent to checking how much the number of gestural alignment changes when the number of lexical alignment changes from 0 to the mean, while holding other predictors constant.

The proportion of gestural alignment explained by lexical alignment can be calculated by dividing the effect size on the count scale by the predicted number of gestural alignment (i.e., intercept).

```{r}
### draw posterior samples for the fixed effects
post_sample = as_draws_df(model) %>% 
  as_tibble() %>% 
  dplyr::select(starts_with("b_"))


### calculate the effect size of lexical alignment on the count scale
lex_align_0_c = 0 - mean(df_trial_info$num_lex_align)

intercept = exp(post_sample$b_Intercept) 
lex_0 = exp(post_sample$b_Intercept + 
              post_sample$b_lex_align_c * lex_align_0_c)

lex_effect_size_count = intercept - lex_0

# summary of the effect size on the count scale (mean, median, 95% credible interval)
effect_size_count_summary = data_frame(
  mean = mean(lex_effect_size_count),
  median = median(lex_effect_size_count),
  ci_lower = quantile(lex_effect_size_count, 0.025),
  ci_upper = quantile(lex_effect_size_count, 0.975))
effect_size_count_summary


### calculate the proportion of gestural alignment explained by lexical alignment
effect_size_prop = lex_effect_size_count / intercept
effect_size_prop_summary = data_frame(
  mean = mean(effect_size_prop),
  median = median(effect_size_prop),
  ci_lower = quantile(effect_size_prop, 0.025),
  ci_upper = quantile(effect_size_prop, 0.975))
effect_size_prop_summary


### generate model predictions per condition
df_pred = post_sample %>% 
  mutate(SymAV = exp(b_Intercept + 1/3*b_conditionAO_Asym + 2/3*b_conditionAsym_Sym),
         AsymAV = exp(b_Intercept + 1/3*b_conditionAO_Asym - 1/3*b_conditionAsym_Sym),
         AO = exp(b_Intercept -2/3*b_conditionAO_Asym -1/3*b_conditionAsym_Sym)) %>% 
  dplyr::select(SymAV, AsymAV, AO) %>%
  pivot_longer(cols = everything(), 
               names_to = "condition", values_to = "predicted") %>%
  mutate(condition = factor(condition, 
                            levels = c("SymAV", "AsymAV", "AO"))) %>% 
  group_by(condition) %>%
  summarize(mean = mean(predicted),
            median = median(predicted),
            ci_lower = quantile(predicted, 0.025),
            ci_upper = quantile(predicted, 0.975))

df_pred
```

On average, 16.3% of gestural alignment can be explained by lexical alignment, with a 95% credible interval of [12.5%, 19.9%]. This suggests that lexical alignment is an important predictor of gestural alignment, but it is not the only factor that contributes to gestural alignment.

<br>

### 7.2.8 Visualize model predictions together with data
```{r}
bp_mean_gest_alignment_model = 
  bp_mean_gest_alignment +
  geom_ribbon(data = df_pred,
              aes(x = condition, y = mean, 
                  ymin = ci_lower, ymax = ci_upper, group = 1),
              fill = "black", alpha = 0.2) +
  geom_line(data = df_pred,
            aes(x = condition, y = mean, group = 1),
            color = "black", size = 0.8)

bp_mean_gest_alignment_model
```

The misalignment between the descriptive statistics (based on mean per pair) and the model predictions (based on mean per trial) arises because mixed-effects models regularizes the estimates for each pair and trial towards the overall mean, especially when the number of trials for a pair is small or when the participant shows extreme values (e.g., very high or low number of gestural alignment). This is actually a good property of mixed-effects models, as it prevents overfitting and provides more accurate estimates of the fixed effects.

Despite the misalignment, our primary goal of this modeling was to estimate the effect of lexical alignment on gestural alignment while controlling for other predictors, so we will proceed with this model.

<br>

******************************


# 8. Correlation btw lexical and gestural alignment
```{r}
cor = pcor.test(df_trial_info$lex_align_c, 
                df_trial_info$num_gestural_align,
                df_trial_info$log_round_c)
cor
```

<br>

******************************


# 9. Gestural alignment rate per iconic gestures (n_gest_alignment / n_iconic)
We can analyze the proportion of gestural alignment in two ways: (1) modeling the rate of gestural alignment per iconic gesture using a negative binomial regression model and (2) modeling the probability of gestural alignment using a zero-one-inflated beta regression model.

Key differences in the two models are that the negative binomial regression model assumes that the rate of gestural alignment is a count variable, while the zero-one-inflated beta regression model assumes that the proportion of gestural alignment is a continuous variable bounded between 0 and 1. Also, while negative binomial regression models the rate of events, the zero-one-inflated beta regression models the probability of events. In the case of the proportion of gestural alignment, two models should yield similar results, but it is important to note that the two models are conceptually different.

As it is a common practice to analyze the frequency measures (e.g., number of gestures) as rates, we will use negative binomial regressions.

<br>

## 9.1 DataViz: proportion of gestural alignment
### bp: mean by condition
```{r bp_mean_prop_cond}
bp_mean_gest_alignment_prop_by_cond = 
  ggplot(data=trial_info_pair, 
         aes(x=condition, y=mean_gest_align_prop, fill=condition)) +
  geom_jitter(aes(color = pair), 
              size = 1, alpha = 1, 
              width = 0.07, height = 0) +
  geom_boxplot(width = .3,
               outlier.shape = NA, alpha = 0.7) +
  geom_point(data = trial_info_cond, 
             aes(y = mean_gest_align_prop), 
             shape = 21, size = 3, fill = "white") +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  labs(x = "Visibility",
       y = "Mean gest align rate") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines"))

interactive_plot(bp_mean_gest_alignment_prop_by_cond)
```

```{r, include=FALSE, echo=FALSE}
ggsave(file="figures/speakerB/gest_alignment/bp_mean_prop_cond.svg", width=4, height=3.5)
```

<br>

### bp: mean by condition and round
```{r bp_mean_prop_cond_round}
pd = position_dodge(width = .75)

bp_mean_gest_alignment_prop_by_round_cond = 
  ggplot(data=trial_info_pair_round, 
         aes(x=round_n, y=mean_gest_align_prop, fill = condition)) +
  geom_jitter(aes(color = pair), 
              size = 0.5, alpha = 0.7, 
              width = 0.07, height = 0) +
  geom_boxplot(width = .5,
               outlier.shape = NA, alpha = 0.7) +
  geom_point(data = trial_info_cond_round, 
             aes(y = mean_gest_align_prop),
             position = pd,
             shape = 21, size = 2, fill = "white") +
  scale_fill_manual(values = c("#ED6B06", "#00786A", "darkgrey")) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(x = "Round",
       y = "Mean gest align rate") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 14, face = 'bold'),
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  facet_grid(cols = vars(condition))

interactive_plot(bp_mean_gest_alignment_prop_by_round_cond)
```

```{r, include=FALSE, echo=FALSE}
ggsave(file="figures/speakerB/gest_alignment/bp_mean_prop_cond_round.svg", width=6.5, height=3.5, dpi=600)
```

<br>



## 9.2 Prepare data
To model the proportion of gestural alignment, we need to remove trials where the number of iconic gestures is 0. This is because dividing any numbers by 0 results in an undefined value (NA) and prevents model from running.
```{r}
df_gest_align_posreg_prop = df_trial_info %>%
  filter(num_iconic_gestures > 0)

### N. rows before removing trails with no iconic gestures
nrows_before = df_trial_info %>% 
  group_by(condition) %>% 
  summarize(n_trials_before = n()) %>% 
  ungroup()

nrows_after = df_gest_align_posreg_prop %>% 
  group_by(condition) %>% 
  summarize(n_trials_after = n()) %>% 
  ungroup()

nrows_removed = left_join(nrows_before, nrows_after) %>% 
  mutate(n_trials_removed = n_trials_before - n_trials_after)

nrows_removed

print(paste0("Number of rows before removing trials with no iconic gestures: ", 
             nrow(df_trial_info)))
print(paste0("Number of rows after removing trials with no iconic gestures: ",
             nrow(df_gest_align_posreg_prop)))
print(paste0("Number of removed trials: ", 
             nrow(df_trial_info) - nrow(df_gest_align_posreg_prop)))
```

<br>

## 9.3 Negative binomial regression models
### 9.3.1 Prior specification
We will set priors based on Akamine et al. (2024). As mentioned in the previous analysis, they detected 4413 iconic gestures and 1086 instances of gestural alignment. Dividing the number of gestural alignment by the number of iconic gestures gives 0.25 (1086/4413) (-1.39 on the log scale). This means that we expect 1 gestural alignment per 4 iconic gestures.

For the slope parameters, we set the mean of 0 with a SD of 0.5. This means that for example, we expect the mean difference between the AO and AsymAV conditions to range from -0.16 to 0.43.

```{r}
### pair
priors_rint_gest_align_prop = c(
  prior(normal(-1.39, 0.5), class = Intercept),
  prior(normal(0, 0.5), class = b),
  prior(normal(0, 50), class = shape),
  prior(normal(0, 0.5), class = sd))

priors_rslope_gest_align_prop = c(
  prior(normal(-1.39, 0.5), class = Intercept),
  prior(normal(0, 0.5), class = b),
  prior(normal(0, 50), class = shape),
  prior(normal(0, 0.5), class = sd),
  prior(lkj(2), class = cor))

priors_rslope_gest_align_prop_zinb = c(
  prior(normal(-1.39, 0.5), class = Intercept),
  prior(normal(0, 0.5), class = b),
  prior(normal(0, 0.5), class = sd),
  prior(lkj(2), class = cor),
  prior(normal(0, 0.5), class = zi), # on the logit scale
  prior(normal(0, 50), class = shape))
```


<br>



### 9.3.2 Model comparison
#### Round
```{r}
nb_align_rate_cond_round = brm(num_gestural_align | rate(num_iconic_gestures) ~ 
                                 1 + condition * round + lex_align_c + role +
                                 (1+round|pair) + (1|target),
                               family = negbinomial(),
                               prior = priors_rslope_gest_align_prop,
                               data = df_gest_align_posreg_prop,
                               sample_prior = T,
                               save_pars = save_pars(all = TRUE),
                               warmup = nwu, iter = niter,
                               control = list(adapt_delta = 0.9, 
                                              max_treedepth = 15),
                               file = "models/speakerB/gest_alignment/nb_align_rate_cond_round")

nb_align_rate_cond_round_c = brm(num_gestural_align | rate(num_iconic_gestures) ~ 
                                   1 + condition * round_c + lex_align_c + role +
                                   (1+round_c|pair) + (1|target),
                                 family = negbinomial(),
                                 prior = priors_rslope_gest_align_prop,
                                 data = df_gest_align_posreg_prop,
                                 sample_prior = T,
                                 save_pars = save_pars(all = TRUE),
                                 warmup = nwu, iter = niter,
                                 control = list(adapt_delta = 0.9, 
                                                max_treedepth = 15),
                                 file = "models/speakerB/gest_alignment/nb_align_rate_cond_round_c")

nb_align_rate_cond_round_log = brm(num_gestural_align | rate(num_iconic_gestures) ~ 
                                     1 + condition * log_round_c + lex_align_c + role +
                                     (1+log_round_c|pair) + (1|target),
                                   family = negbinomial(),
                                   prior = priors_rslope_gest_align_prop,
                                   data = df_gest_align_posreg_prop,
                                   sample_prior = T,
                                   save_pars = save_pars(all = TRUE),
                                   warmup = nwu, iter = niter,
                                   control = list(adapt_delta = 0.9, 
                                                  max_treedepth = 15),
                                   file = "models/speakerB/gest_alignment/nb_align_rate_cond_round_log")



### loo compare
if (!file.exists("models/speakerB/gest_alignment/loo_nb_align_rate_cond_round.rds")){
  nb_cond_round_loo = loo(nb_align_rate_cond_round)
  saveRDS(nb_cond_round_loo, file = "models/speakerB/gest_alignment/loo_nb_align_rate_cond_round.rds")
}

if (!file.exists("models/speakerB/gest_alignment/loo_nb_align_rate_cond_round_c.rds")){
  nb_cond_round_c_loo = loo(nb_align_rate_cond_round_c)
  saveRDS(nb_cond_round_c_loo, file = "models/speakerB/gest_alignment/loo_nb_align_rate_cond_round_c.rds")
}

if (!file.exists("models/speakerB/gest_alignment/loo_nb_align_rate_cond_round_log.rds")){
  nb_cond_round_log_loo = loo(nb_align_rate_cond_round_log)
  saveRDS(nb_cond_round_log_loo, file = "models/speakerB/gest_alignment/loo_nb_align_rate_cond_round_log.rds")
}

nb_cond_round_loo = readRDS("models/speakerB/gest_alignment/loo_nb_align_rate_cond_round.rds")
nb_cond_round_c_loo = readRDS("models/speakerB/gest_alignment/loo_nb_align_rate_cond_round_c.rds")
nb_cond_round_log_loo = readRDS("models/speakerB/gest_alignment/loo_nb_align_rate_cond_round_log.rds")

loo_compare(nb_cond_round_loo, nb_cond_round_c_loo, nb_cond_round_log_loo)
```

The leave-one-out (LOO) Effect shows that the backward-difference coded round provides a far larger predictive power (elpd_diff) and a far smaller standard error (se_diff) compared to the centered round or centered log-transformed round. Thus, we will use the bd coded round as a predictor for further analyses.

<br>

#### ZI or not
```{r}
zinb_align_rate_cond_round = brm(num_gestural_align ~ 
                                   1 + condition * round + lex_align_c + role +
                                   offset(log(num_iconic_gestures)) +
                                   (1+round|pair) + (1|target),
                                 family = zero_inflated_negbinomial(),
                                 prior = priors_rslope_gest_align_prop_zinb,
                                 data = df_gest_align_posreg_prop,
                                 sample_prior = T,
                                 warmup = nwu, iter = niter,
                                 control = list(adapt_delta = 0.9, 
                                                max_treedepth = 15),
                                 file = "models/speakerB/gest_alignment/zinb_align_rate_cond_round")


### loo compare
if (!file.exists("models/speakerB/gest_alignment/loo_zinb_align_rate_cond_round.rds")){
  zinb_cond_round_c_loo = loo(zinb_align_rate_cond_round)
  saveRDS(zinb_cond_round_c_loo, file = "models/speakerB/gest_alignment/loo_zinb_align_rate_cond_round.rds")
}

nb_cond_round_c_loo = readRDS("models/speakerB/gest_alignment/loo_nb_align_rate_cond_round.rds")
zinb_cond_round_c_loo = readRDS("models/speakerB/gest_alignment/loo_zinb_align_rate_cond_round.rds")

loo_compare(nb_cond_round_c_loo, zinb_cond_round_c_loo)
```

The loo comparsion shows that non-inflation model has a higher predictive power than the zero-inflation model. As such, we will use NB regression models for further analyses.

<br>

### 9.3.3 Prior predictive check
```{r pp_check_rate}
nb_gest_align_prop_prior = brm(num_gestural_align | rate(num_iconic_gestures) ~
                                 1 + condition + round + lex_align_c + role +
                                 (1+round|pair) + (1|target),
                               family = negbinomial(),
                               prior = priors_rslope_gest_align_prop,
                               data = df_gest_align_posreg_prop,
                               sample_prior = "only",
                               control = list(adapt_delta = 0.9, 
                                              max_treedepth = 20),
                               file = "models/speakerB/gest_alignment/nb_gest_align_prop_prior")

pp_check(nb_gest_align_prop_prior, ndraws = 100, 
         type = "bars_grouped", group = "condition") +
  coord_cartesian(xlim = c(0, 10))
```

The prior predictive check shows that the model generates data that are somewhat similar to the observed data, demonstrating that the priors are reasonable.

<br>

### 9.3.4 Fit the model
```{r}
nb_align_rate_cond_round = 
  brm(num_gestural_align | rate(num_iconic_gestures) ~ 
        1 + condition * round + lex_align_c + role +
        (1+round|pair) + (1|target),
      family = negbinomial(),
      prior = priors_rslope_gest_align_prop,
      data = df_gest_align_posreg_prop,
      sample_prior = T,
      save_pars = save_pars(all = TRUE),
      warmup = nwu, iter = niter,
      control = list(adapt_delta = 0.9, 
                     max_treedepth = 15),
      file = "models/speakerB/gest_alignment/nb_align_rate_cond_round")

model = nb_align_rate_cond_round
summary(model)
# bayestestR::hdi(model)
# bayestestR::hdi(model, ci = 0.89)
```

The coefficients show that the proportion of gestural alignment was significantly higher in the SymAV condition than in the AO condition. Also, the rate of gestural alignment significantly increased from R1--R2 and R2--R3 and stabilized afterwards.

<br>

### 9.3.5 Posterior predictive check
```{r ppd_rate}
pp_check(model, ndraws = 100, 
         type = "bars_grouped", group = "condition") +
  coord_cartesian(xlim = c(0, 5))

pp_check(model, ndraws = 100, 
         type = "bars_grouped", group = "round") +
  coord_cartesian(xlim = c(0, 5))
```

Although the model prediction is not perfect, this model had a higher predictive power than the zero-inflated negative binomial model and generates data that are quite similar to the observations. As such, we will use this model.

<br>

### 9.3.6 Posterior distributions
```{r post_rate, fig.width=10, fig.height=4}
df_post_beta_lex = posterior_beta(zinb_align_cond_round, 
                                  round_int = FALSE, lex_int = TRUE) %>% 
  dplyr::select(.chain, .draw, .variable, .value) %>%
  filter(grepl("N. lex align", .variable)) %>% 
  mutate(component = "N. lex align")

df_post_beta = posterior_beta(model) %>% 
  dplyr::select(-.iteration, -b_role1)

# replace the lex_align_c coefficient with the one from the model on count data
df_post_beta_new = df_post_beta %>% 
  filter(!grepl("N. lex align", .variable)) %>%
  rbind(., df_post_beta_lex)

# summarize the posterior distribution
post_beta_summary = df_post_beta_new %>%
  group_by(.variable) %>%
  summarize(mean = mean(.value),
            est_error = sd(.value),
            lci = quantile(.value, 0.025),
            uci = quantile(.value, 0.975))
post_beta_summary

# visualize the posterior distribution
p_pd = plot_posterior(df_post_beta_new, interaction = F,
                      title = "C. Posterior distributions for the effects on gestural alignment",
                      xlim_cond = 1.5, xlim_round = 2, 
                      xlim_lex = 0.4, ncol_wrap = 3)
p_pd
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/gest_alignment/posterior_prop_nb.svg", width=10, height=4)
```

<br>

### 9.3.7 Prior-posterior update plot
```{r update_rate, width=10, height=4}
post_sample_lex = as_draws_df(zinb_align_cond_round) %>% 
  as_tibble() %>% 
  dplyr::select(starts_with("b_lex_align_c") | "prior_b_lex_align_c") %>% 
  mutate(ao_sym_lex = `b_lex_align_c:conditionAO_Asym` + `b_lex_align_c:conditionAsym_Sym`)

post_sample = as_draws_df(model) %>% 
  as_tibble() %>% 
  dplyr::select(!starts_with(c("r_", "sd_", "cor_", "z_", "L_"))) %>% 
  mutate(ao_sym = b_conditionAO_Asym + b_conditionAsym_Sym,
         ao_sym_round12 = `b_conditionAO_Asym:roundR12` + `b_conditionAsym_Sym:roundR12`,
         ao_sym_round23 = `b_conditionAO_Asym:roundR23` + `b_conditionAsym_Sym:roundR23`,
         ao_sym_round34 = `b_conditionAO_Asym:roundR34` + `b_conditionAsym_Sym:roundR34`,
         ao_sym_round45 = `b_conditionAO_Asym:roundR45` + `b_conditionAsym_Sym:roundR45`,
         ao_sym_round56 = `b_conditionAO_Asym:roundR56` + `b_conditionAsym_Sym:roundR56`,
         prior_lex_align = post_sample_lex$prior_b_lex_align_c,
         lex_align = post_sample_lex$b_lex_align_c,
         ao_asym_lex = post_sample_lex$`b_lex_align_c:conditionAO_Asym`, 
         asym_sym_lex = post_sample_lex$`b_lex_align_c:conditionAsym_Sym`)

pp_update_rate = pp_update_plot(post_sample, model_type="nb", fam_par=FALSE, ncol=5)
pp_update_rate
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/gest_alignment/pp_update_rate.svg", width=10, height=4)
```

<br>

### 9.3.8 Hypothesis testing: Bayes factor
```{r}
### varying priors for sensitivity analysis
prior_size = c("xs", "s", "m", "l", "xl")
prior_sd = c(0.1, 0.3, 0.5, 0.7, 1)


### list of hypotheses
hps = c("conditionAO_Asym = 0", "conditionAsym_Sym = 0",
       "conditionAO_Asym + conditionAsym_Sym = 0",
       "roundR12 = 0", "roundR23 = 0", "roundR34 = 0", 
       "roundR45 = 0", "roundR56 = 0",
       "conditionAO_Asym:roundR12 = 0", "conditionAO_Asym:roundR23 = 0",
       "conditionAO_Asym:roundR34 = 0", "conditionAO_Asym:roundR45 = 0", 
       "conditionAO_Asym:roundR56 = 0",
       "conditionAsym_Sym:roundR12 = 0", "conditionAsym_Sym:roundR23 = 0",
       "conditionAsym_Sym:roundR34 = 0", "conditionAsym_Sym:roundR45 = 0", 
       "conditionAsym_Sym:roundR56 = 0",
       "conditionAO_Asym:roundR12 + conditionAsym_Sym:roundR12 = 0",
       "conditionAO_Asym:roundR23 + conditionAsym_Sym:roundR23 = 0",
       "conditionAO_Asym:roundR34 + conditionAsym_Sym:roundR34 = 0",
       "conditionAO_Asym:roundR45 + conditionAsym_Sym:roundR45 = 0",
       "conditionAO_Asym:roundR56 + conditionAsym_Sym:roundR56 = 0")
effects = c("AO--AsymAV", "AsymAV--SymAV", "AO--SymAV",
            "R1--R2", "R2--R3", "R3--R4", "R4--R5", "R5--R6",
            "AO--AsymAV:R1--R2", "AO--AsymAV:R2--R3", "AO--AsymAV:R3--R4",
            "AO--AsymAV:R4--R5", "AO--AsymAV:R5--R6",
            "AsymAV--SymAV:R1--R2", "AsymAV--SymAV:R2--R3", "AsymAV--SymAV:R3--R4",
            "AsymAV--SymAV:R4--R5", "AsymAV--SymAV:R5--R6",
            "AO--SymAV:R1--R2", "AO--SymAV:R2--R3", "AO--SymAV:R3--R4", 
            "AO--SymAV:R4--R5", "AO--SymAV:R5--R6")

for (i in 1:length(prior_sd)){
  priors = c(
    prior(normal(-1.39, 0.5), class = Intercept),
    set_prior(paste0("normal(0,", prior_sd[i], ")"), class = "b"),
    prior(normal(0, 0.5), class = sd),
    prior(lkj(2), class = cor),
    prior(normal(0, 50), class = shape))
  
  fname = paste0("models/speakerB/gest_alignment/nb_align_rate_cond_round_", prior_size[i])
  fname = gsub("_m", "", fname) # remove "_m" for the medium prior
  
  fit = brm(num_gestural_align | rate(num_iconic_gestures) ~ 
              1 + condition * round + lex_align_c + role +
              (1+round|pair) + (1|target),
            family = negbinomial(),
            prior = priors,
            data = df_gest_align_posreg_prop,
            sample_prior = T,
            save_pars = save_pars(all = TRUE),
            warmup = nwu, iter = niter,
            control = list(adapt_delta = 0.9, 
                           max_treedepth = 15),
            file = fname)
  
  ### compute BFs for all hypotheses and store them as dataframe
  for (j in 1:length(hps)){
    h = hypothesis(fit, hps[j])
    # transform the result to dataframe
    result = data_frame(h$hypothesis) %>%
      mutate(size = prior_size[i],
             sd = prior_sd[i],
             Effect = effects[j])
    # combine the result
    if (i==1 & j==1){
      df_results = result
    } else {
      df_results = rbind(df_results, result)}
  }
}

df_bf_rate = df_results %>%
  mutate(prior = paste0("N(0, ", sd, ")"),
         BF10 = 1 / abs(Evid.Ratio),
         Effect = factor(Effect,
                         levels = effects),
         Predictor = factor(case_when(grepl(":R", Effect) ~ "Interaction",
                                      grepl("R", Effect) ~ "Round",
                                      .default = "Visibility"),
                            levels = c("Visibility", "Round", "Interaction")),
         across(where(is.numeric), ~ round(., 3)),
         Star = ifelse(BF10 >= 30 | BF10 <= 1/30, "***",
                       ifelse(BF10 >= 10 | BF10 <= 1/10, "**",
                              ifelse(BF10 >= 3 | BF10 <= 1/3, "*", ""))),
         Star = ifelse(BF10 < 1, str_replace_all(Star, "[*]", "="), Star)) %>% 
  dplyr::select(size, sd, prior, Effect, Predictor,
                Estimate, Est.Error, `CI.Lower`, `CI.Upper`, BF10, Star) %>% 
  arrange(Effect, sd)


# add the results for lexical alignment
df_bf = rbind(df_bf_rate, df_bf_lex) %>% 
   mutate(Predictor = factor(case_when(grepl("align", Effect) ~ "N. lex align",
                                       grepl("R", Effect) ~ "Round",
                                      .default = "Visibility"),
                            levels = c("Visibility", "Round", "N. lex align")))
df_bf
```

```{r p_bf_rate, fig.width=13, fig.height=4}
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
col_vector = c("#00786A", "#ED6B06", col_vector)

### Plot BFs ###
p_bf_rate = 
  ggplot(filter(df_bf, !Effect %in% c("R1--R2", "N. lex align")), 
              aes(x = factor(sd), y = BF10, group = Effect)) +
  geom_hline(yintercept = 1, linetype="dashed") +
  geom_point(aes(color=Effect)) +
  geom_line(aes(color=Effect)) +
  labs(x = "SD for the prior",
       title = "D. Bayes factors for the effects on gestural alignment") +
  scale_color_manual(values = col_vector) +
  facet_wrap(vars(Predictor), scale = "free_x") +
  theme_clean(base_size = 15) +
  theme(axis.text.x = element_text(colour = "black", size = 14),
        axis.text.y = element_text(colour = "black", size = 14),
        axis.title = element_text(size = 13, face = 'bold'),
        axis.title.x = element_text(vjust = -2),
        axis.title.y = element_text(vjust = 2),
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 10.5),
        strip.text = element_text(size = 14, face = 'bold'),
        strip.background = element_blank(),
        plot.title.position = "plot", # left align the title
        plot.background = element_blank(),
        plot.margin = unit(c(1.1,1.1,1.1,1.1), "lines")) +
  scale_y_log10("Bayes factor (BF10)",
                # limits = c(0.03, 30000),
                breaks = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100, 1e3, 1e4),
                labels = c(0.001, 0.03, 0.01, 0.1, 0.33, 1, 3, 10, 30, 100, 1e3, 1e4)) +
  guides(color = guide_legend(ncol=2))

p_bf_rate
```

```{r, include=FALSE, echo=FALSE}
ggsave("figures/speakerB/gest_alignment/bf_rate.svg", width=10, height=6)
```

<br>

### 9.3.9 Back-transformation
We back-transform the posterior samples to the original scale to visualize the predicted proportion of gestural alignment across conditions and rounds.

We defined the regression as follows (only including condition and round predictors for simplicity):
$$
\begin{align*}
  gest\_align\_rate = 
  exp(&\beta_0 + (\beta_{AO\_Asym} \times AO\_Asym) + (\beta_{Asym\_Sym} \times Asym\_Sym) + \\
  &(\beta_{R12} \times R12) + (\beta_{R23} \times R23) + (\beta_{R34} \times R34) + (\beta_{R45} \times R45) + (\beta_{R56} \times R56) \\
  &(\beta_{AO\_Asym:R12} \times AO\_Asym \times R12) + (\beta_{AO\_Asym:R23} \times AO\_Asym \times R23) + \\
  &(\beta_{AO\_Asym:R34} \times AO\_Asym \times R34) + (\beta_{AO\_Asym:R45} \times AO\_Asym \times R45) + \\
  &(\beta_{AO\_Asym:R56} \times AO\_Asym \times R56) + \\
  &(\beta_{Asym\_Sym:R12} \times Asym\_Sym \times R12) + (\beta_{Asym\_Sym:R23} \times Asym\_Sym \times R23) + \\
  &(\beta_{Asym\_Sym:R34} \times Asym\_Sym \times R34) + (\beta_{Asym\_Sym:R45} \times Asym\_Sym \times R45) + \\
  &(\beta_{Asym\_Sym:R56} \times Asym\_Sym \times R56))
  
\end{align*}
$$

The values of the predictors ($x$) are determined by the contrast coding. The contrast matrix is as follows:

**Condition**
|        | AO_Asym | AsymAV_Sym |
| SymAV  | 1/3     | 2/3        |
| AsymAV | 1/3     | -1/3       |
| AO     | -2/3    | -1/3       |

**Round**
|    | R12  | R23  | R34  | R45  | R56  |
| R1 | -5/6 | -2/3 | -1/2 | -1/3 | -1/6 |
| R2 | 1/6  | -2/3 | -1/2 | -1/3 | -1/6 |
| R3 | 1/6  | 1/3  | -1/2 | -1/3 | -1/6 |
| R4 | 1/6  | 1/3  | 1/2  | -1/3 | -1/6 |
| R5 | 1/6  | 1/3  | 1/2  | 2/3  | -1/6 |
| R6 | 1/6  | 1/3  | 1/2  | 2/3  | 5/6  |

Given that 0 represents the ground mean in these coding, we can compute the estimated marginal mean for each condition like this:

$SymAV = \beta_0 + \beta_{AO\_Asym} \times 1/3) + (\beta_{Asym\_Sym} \times 2/3)$

Note that because (i) the marginal mean for each condition can be calculated by averaging over the conditional means of the 6 rounds in that condition, and (ii) 0 represents the ground mean in the contrast coding, the estimated marginal mean for each condition can be calculated by simply plugging in the contrast values for the condition predictors and setting the round predictors to 0. And because multiplying any number by 0 results in 0, we can remove all the terms involving round predictors and their interactions with condition predictors.

```{r}
#### visibility effects ####
alpha = post_sample$b_Intercept
b_ao_asym = post_sample$b_conditionAO_Asym
b_asym_sym = post_sample$b_conditionAsym_Sym
b_round12 = post_sample$b_roundR12
b_round23 = post_sample$b_roundR23
b_round34 = post_sample$b_roundR34
b_round45 = post_sample$b_roundR45
b_round56 = post_sample$b_roundR56
b_ao_asym_round12 = post_sample$`b_conditionAO_Asym:roundR12`
b_ao_asym_round23 = post_sample$`b_conditionAO_Asym:roundR23`
b_ao_asym_round34 = post_sample$`b_conditionAO_Asym:roundR34`
b_ao_asym_round45 = post_sample$`b_conditionAO_Asym:roundR45`
b_ao_asym_round56 = post_sample$`b_conditionAO_Asym:roundR56`
b_asym_sym_round12 = post_sample$`b_conditionAsym_Sym:roundR12`
b_asym_sym_round23 = post_sample$`b_conditionAsym_Sym:roundR23`
b_asym_sym_round34 = post_sample$`b_conditionAsym_Sym:roundR34`
b_asym_sym_round45 = post_sample$`b_conditionAsym_Sym:roundR45`
b_asym_sym_round56 = post_sample$`b_conditionAsym_Sym:roundR56`


### convert the samples to the original scale based on the contrast matrix
cmax_cond = contrasts(df_gest_align_posreg_prop$condition)
cmax_cond
cmax_round = contrasts(df_gest_align_posreg_prop$round)
cmax_round

i = 1
conds = c("SymAV", "AsymAV", "AO")
df_pred = tibble()
df_pred_int = tibble()

for (i in 1:length(conds)){
  condition = conds[i]
  pred = exp(alpha + b_ao_asym * cmax_cond[i,1] + b_asym_sym * cmax_cond[i,2])
  df_pred = rbind(df_pred, tibble(condition = factor(condition), 
                                  mean = mean(pred),
                                  lci = quantile(pred, 0.025),
                                  uci = quantile(pred, 0.975)))
  for (j in 1:6){
    round = j
    pred = exp(alpha + 
                 # condition
                 b_ao_asym * cmax_cond[i,1] + b_asym_sym * cmax_cond[i,2] +
                 # round
                 b_round12 * cmax_round[j,1] + b_round23 * cmax_round[j,2] + 
                 b_round34 * cmax_round[j,3] + b_round45 * cmax_round[j,4] + 
                 b_round56 * cmax_round[j,5] +
                 # condition * round
                 b_ao_asym_round12 * cmax_cond[i,1] * cmax_round[j,1] +
                 b_ao_asym_round23 * cmax_cond[i,1] * cmax_round[j,2] +
                 b_ao_asym_round34 * cmax_cond[i,1] * cmax_round[j,3] +
                 b_ao_asym_round45 * cmax_cond[i,1] * cmax_round[j,4] +
                 b_ao_asym_round56 * cmax_cond[i,1] * cmax_round[j,5] +
                 b_asym_sym_round12 * cmax_cond[i,2] * cmax_round[j,1] +
                 b_asym_sym_round23 * cmax_cond[i,2] * cmax_round[j,2] +
                 b_asym_sym_round34 * cmax_cond[i,2] * cmax_round[j,3] +
                 b_asym_sym_round45 * cmax_cond[i,2] * cmax_round[j,4] +
                 b_asym_sym_round56 * cmax_cond[i,2] * cmax_round[j,5])
    
    df_pred_int = rbind(df_pred_int, tibble(condition = factor(condition),
                                            round = factor(round),
                                            mean = mean(pred),
                                            lci = quantile(pred, 0.025),
                                            uci = quantile(pred, 0.975)))}
}

df_pred
df_pred_int
```

<br>

### 9.3.10 Calculate effect size
```{r effect_size_rate}
# calculate the difference between AsymAV and AO
pred_asym = exp(alpha + b_ao_asym * cmax_cond[2,1] + b_asym_sym * cmax_cond[2,2])
pred_ao = exp(alpha + b_ao_asym * cmax_cond[3,1] + b_asym_sym * cmax_cond[3,2])
effect_size_rate = pred_asym - pred_ao

# summary of the effect size (mean, median, 95% credible interval)
effect_size_rate_summary = data_frame(
  mean = mean(effect_size_rate),
  median = median(effect_size_rate),
  ci_lower = quantile(effect_size_rate, 0.025),
  ci_upper = quantile(effect_size_rate, 0.975))
effect_size_rate_summary

### calculate the proportion of gestural alignment explained by the visibility
effect_size_prop = effect_size_rate / pred_asym
effect_size_prop_summary = data_frame(
  mean = mean(effect_size_prop),
  median = median(effect_size_prop),
  ci_lower = quantile(effect_size_prop, 0.025),
  ci_upper = quantile(effect_size_prop, 0.975))
effect_size_prop_summary
```

On average, 37.8% of gestural alignment can be explained by lexical alignment, with a 95% credible interval of [1.7%, 62.5%]. This suggests that gesture-to-gesture priming is an important predictor of gestural alignment. However, the credible interval is quite wide, indicating a high level of uncertainty in this estimate.

In the previous analysis, we found that on average, 16.3% [12.5%, 19.9%] of gestural alignment can be explained by lexical alignment. This suggests that priming and lexical alignment can only account for 54.1% (= 37.8% + 16.3%) of gestural alignment, leaving a large portion of gestural alignment unexplained by these two factors. This underscores the importance of investigating other potential predictors of gestural alignment and the need to move beyond dichotomous thinking about whether gestural alignment is due to priming or communicative functions. Instead, we should consider the possibility that gestural alignment is a complex phenomenon that can be influenced by multiple factors.

<br>

### 9.3.11 Visualize the model estimates
```{r}
### visibility
bp_mean_gest_alignment_prop_model = 
  bp_mean_gest_alignment_prop_by_cond +
  geom_ribbon(data = df_pred,
              aes(x = condition, y = mean, 
                  ymin = lci, ymax = uci, group = 1),
              fill = "black", alpha = 0.2) +
  geom_line(data = df_pred,
            aes(x = condition, y = mean, group = 1),
            color = "black", size = 0.8) +
  labs(title = "A. Gest align rate across visibility") +
  theme(plot.title.position = "plot")

bp_mean_gest_alignment_prop_model
ggsave("figures/speakerB/gest_alignment/bp_mean_prop_cond_model.svg", width=4, height=4)


### visibility x round
bp_mean_gest_alignment_prop_by_round_cond_model = 
  bp_mean_gest_alignment_prop_by_round_cond +
  geom_ribbon(data = df_pred_int,
              aes(x = round, y = mean, 
                  ymin = lci, ymax = uci, group = condition),
              fill = "black", alpha = 0.2) +
  geom_line(data = df_pred_int,
            aes(x = round, y = mean, group = condition),
            color = "black", size = 0.8) +
  labs(title = "B. Gest align rate across visibility and round") +
  theme(plot.title.position = "plot")

bp_mean_gest_alignment_prop_by_round_cond_model
ggsave("figures/speakerB/gest_alignment/bp_mean_prop_cond_round_model.svg", width=8, height=4)
```

<br>

# 10. Merge plots
```{r merge_plots, fig.width=12, fig.height=13}
design = "AAAABBBBBB
          CCCCCCCCCC
          DDDDDDDDDD"

free(bp_mean_gest_alignment_prop_model) + #A
  bp_mean_gest_alignment_prop_by_round_cond_model + #B
  free(p_pd) + #C
  free(p_bf_rate) + #D
  plot_layout(design = design,
              heights = c(0.6,1,1))

# save the plot
ggsave("figures/speakerB/gest_alignment/gest_align_combined.svg", width=12, height=13)
```


******************************

# =====Extra: Understanding contrast coding=====
Here, we will understand three-level contrast coding by simulating some data and fitting a linear regression.

## Linear regression with three conditions
### Simulate data
```{r}
### defining parameters
conditions = c("cond1", "cond2", "cond3")
b12 = 200
b23 = -300
mean1 = 400
mean2 = mean1 + b12
mean3 = mean2 + b23

### simulating data
n = 1000 # number of observations per condition
sd = 50

y1 = rnorm(n, mean1, sd)
y2 = rnorm(n, mean2, sd)
y3 = rnorm(n, mean3, sd)

df = data.frame(y = c(y1, y2, y3),
                condition = factor(rep(conditions, each=n)))

# check if the data are simulated correctly
df %>% 
  group_by(condition) %>% 
  summarise(mean = mean(y),
            sd = sd(y))

# ground mean
mean(df$y)
```

<br>

### Contrast coding
```{r}
h_cond = hypr(C12 = cond2 ~ cond1,
              C23 = cond3 ~ cond2,
              levels = levels(df$condition))
h_cond

contrasts(df$condition) = contr.hypothesis(h_cond)
```

### Fit the model
```{r}
model = lm(y ~ condition, data = df)
summary(model)
```

There are three things to note here:

1. The intercept (433) is the estimated **ground mean**, not the mean of cond2 (400).
2. The slope for C12 (200) is the estimated difference between cond1 and cond2, and the slope for C23 (-300) is the estimated difference between cond2 and cond3
3. None of the coefficients represent the mean of each condition.

An advantage of this contrast coding is that we can estimate the marginal effects of each condition if we have other predictors in the model. This is because the contrast coding makes the intercept represent the ground mean, which is the average of the three conditions.

A disadvantage of this contrast coding is that the coefficients are not directly interpretable as the mean of each condition. This means that calculating the predicted mean for each condition requires a bit complex calculation compared to treatment coding. However, this is not a big issue because we can easily calculate the predicted mean for each condition using the coefficients from the model and contrast matrix.

<br>

### Calculate the predicted mean for each condition
```{r}
b_intercept = coef(model)[1]
b_C12 = coef(model)[2]
b_C23 = coef(model)[3]

contrasts(df$condition)

pred_cond1 = b_intercept + (b_C12 * -2/3) + (b_C23 * -1/3)
pred_cond2 = b_intercept + (b_C12 * 1/3) + (b_C23 * -1/3)
pred_cond3 = b_intercept + (b_C12 * 1/3) + (b_C23 * 2/3)

# show the predicted means for each condition
tibble(condition = conditions,
       predicted_mean = c(pred_cond1, pred_cond2, pred_cond3))
```

As you can see, the predicted means for each condition can be calculated by multiplying the coefficients with the contrast matrix and adding them to the intercept.

We can also use the `marginaleffects` package to calculate the predicted means for each condition, which is much easier than doing the calculation manually.

```{r}
avg_predictions(model, by = "condition")
```

<br>

## Negbinomial regression with three conditions
Next, we will model count data using a Negative binomial regression. The purpose of this is to understand the behavior of the `avg_predictions()` function. Also, we will add another predictor `round_c` to the model to see how the contrast coding allows us to estimate the marginal effects of each condition.

### Simulate data
```{r}
### defining parameters
conditions = c("cond1", "cond2", "cond3")
round = c(-2.5, -1.5, -0.5, 0.5, 1.5, 2.5) # centered round variable
b12 = 20
b23 = -10
b_round = 5
mean1 = 50

### simulating data
n = 1000 # number of observations per condition
sample_cond = rep(conditions, each = n)
sample_round = rep(round, times = n*3/length(round))
time = rnorm(n*3, 10, 0.5)

y = as.integer(mean1 + ifelse(sample_cond == "cond1", 0, 
                              ifelse(sample_cond == "cond2", b12, b12 + b23)) + 
                 (b_round * sample_round) + rnorm(n*3, 0, 5))

df = data.frame(condition = factor(sample_cond),
                round = sample_round,
                time = time,
                y = y)

# check if the data are simulated correctly
df %>% 
  group_by(condition) %>% 
  summarise(mean = mean(y),
            sd = sd(y),
            mean_rate = mean(y/time),
            sd_rate = sd(y/time))

# ground mean
mean(df$y)
mean(df$y/df$time)
```


### Fit the model
```{r}
### Poisson model without exposure variable
model1 = brm(y ~ 1 + condition * round, 
             prior = c(
               prior(normal(4, 0.5), class = Intercept),
               prior(normal(0, 0.5), class = b),
               prior(normal(0, 50), class = shape)),
             data = df, 
             family = negbinomial(),
             file = "models/speakerB/sim_model1")
summary(model1)

### Poisson model with exposure variable
model2 = brm(y | rate(time) ~ 1 + condition * round,
             prior = c(
               prior(normal(1.5, 0.5), class = Intercept),
               prior(normal(0, 0.5), class = b),
               prior(normal(0, 50), class = shape)),
             data = df, 
             family = negbinomial(),
             file = "models/speakerB/sim_model2")
summary(model2)

### Negbin model with exposure variable
model3 = brm(y ~ 1 + condition * round + offset(log(time)),
             prior = c(
               prior(normal(1.5, 0.5), class = Intercept),
               prior(normal(0, 0.5), class = b),
               prior(normal(0, 50), class = shape)),
             data = df, 
             family = negbinomial(),
             file = "models/speakerB/sim_model3")
summary(model3)
```

It is important to note that the coefficients are identical regardless of whether the exposure variable is specified as `rate()` or `offset()`. Next, we will see that `offset()` actually causes issues when generating predictions using the `avg_predictions()` function.

```{r}
### Negbin model without exposure variable
avg_predictions(model1, by = "condition")
avg_predictions(model1, by = "condition", type = "link")

### Negbin model with rate()
avg_predictions(model2, by = "condition")
avg_predictions(model2, by = "condition", type = "link")
avg_predictions(model2, by = "condition", type = "link", transform = exp)

### Negbin model with offset()
avg_predictions(model3, by = "condition")
avg_predictions(model3, by = "condition", type = "link")
avg_predictions(model3, by = "condition", type = "link", transform = exp)
```

As you can see, the `avg_predictions()` function gives us the predicted mean for each condition on the response scale (i.e., count) by default. There are a few things to keep in mind:

1. When we using the `type = "response"` argument, we always get the predicted mean on the response scale, regardless of whether we have an exposure variable or not.
2. When we using the `type = "link"` argument, the output differs depending on (i) whether we have an exposure variable or not, and (ii) whether we specify it as `rate()` or `offset()`. If we don't have an exposure variable, we get the predicted mean on the link scale (i.e., log count). If we have an exposure variable specified as `rate()`, we get the predicted mean **rate** on the link scale. If we have an exposure variable specified as `offset()`, we get the same predicted mean on the link scale as the model without exposure variable, although the model coefficients are identical to model with rate(). This mismatch is suboptimal because it can lead to incorrect interpretation of the model coefficients and predicted values. Therefore, it is recommended to specify the exposure variable using `rate()` rather than `offset()` whenever possible, but some family (e.g., `zero_inflated_negbinomial()`) does not allow the use of `rate()`, in which case we can specify the exposure variable using `offset()` but we need to be careful when interpreting the model coefficients and predicted values.


<br>

******************************

# =====Session info=====
```{r}
sessionInfo()
```
